### 2024-04-17 paper/paper.qmd
tiny refine

---
title: "Bayesian Insights into Aerial Bombing Strategies: An Ordered Logistic Regression Analysis of WWII Target Prioritization Against Germany"
author: 
  - Yunzhao Li
thanks: "Code and data are available at: https://github.com/yunzhaol/aerial_bomb_priority.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(arrow)
library(knitr)
library(modelsummary)
library(rstanarm)
library(tidyverse)
library(ggplot2)
library(bayesplot)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-cesdata1
#| tbl-cap: "2022 CES (Cooperative Election Study) Data (Cultural)"

# Load in data
# ces2022_1 <- read_csv("data/cleaned_ces2022_1.csv")
# ces2022_2 <- read_csv("data/cleaned_ces2022_2.csv")
# 
# ces2022_1 |>
#   head() |>
#   kable(
#     col.names = c("Voted For (2020)", "Age Group", "Gender", "Education", "Race", "Religion"),
#     booktabs = TRUE
  # )
```

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

# cleaned_aerial_priority <- read_parquet("data/analysis_data/cleaned_aerial_priority.parquet")
# head(cleaned_aerial_priority)
```

```{r}

# analysis_data |> 
#   ggplot(aes(x = width, y = length)) +
#   geom_point(alpha = 0.8) +
#   theme_minimal() +
#   labs(x = "Wing width (mm)",
#        y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

# library(rstanarm)
# 
# first_model <-
#   readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

# modelsummary::modelsummary(
#   list(
#     "First model" = first_model
#   ),
#   statistic = "mad",
#   fmt = 2
# )
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

# pp_check(first_model) +
#   theme_classic() +
#   theme(legend.position = "bottom")
# 
# posterior_vs_prior(first_model) +
#   theme_minimal() +
#   scale_color_brewer(palette = "Set1") +
#   theme(legend.position = "bottom") +
#   coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

# plot(first_model, "trace")
# 
# plot(first_model, "rhat")
```

\newpage

# References

### 2024-04-17 scripts/04-model.R

@@ -21,17 +21,6 @@ set.seed(302)
 sampled_data <- cleaned_aerial_priority %>%
   sample_n(1000)
 
-# Ensure the response is an ordered factor
-sampled_data$tgt_priority_explanation <- factor(
-  sampled_data$tgt_priority_explanation,
-  levels = c("target of last resort", "target of opportunity", "secondary target", "primary target"),
-  ordered = TRUE
-)
-
-# Convert categorical predictors to factors
-sampled_data$tgt_industry <- factor(sampled_data$tgt_industry)
-sampled_data$country_flying_mission <- factor(sampled_data$country_flying_mission)
-
 # Build a Bayesian ordered logistic regression model using stan_polr
 aerial_priority_model <- stan_polr(
   formula = tgt_priority_explanation ~ tgt_industry + country_flying_mission + total_tons + ac_attacking,

### 2024-04-17 paper/paper.qmd
modify model and add some graph in qmd

@@
 library(knitr)
+library(kableExtra)
 library(modelsummary)
@@
 library(bayesplot)
+library(broom)
 ```
@@
 # Load in data
-# ces2022_1 <- read_csv("data/cleaned_ces2022_1.csv")
-# ces2022_2 <- read_csv("data/cleaned_ces2022_2.csv")
-# 
+cleaned_aerial_priority <- read_parquet(here::here("data/analysis_data/cleaned_aerial_priority.parquet"))
+
+# Random sampling if needed
+set.seed(302)
+sampled_data <- cleaned_aerial_priority %>%
+  sample_n(3000)
+
 # ces2022_1 |>
@@
 
-# library(rstanarm)
-# 
-# first_model <-
-#   readRDS(file = here::here("models/first_model.rds"))
+# Load in models
+aerial_priority_model <-
+  readRDS(file = here::here("models/aerial_priority_model.rds"))
 ```
@@
 
-# modelsummary::modelsummary(
-#   list(
-#     "First model" = first_model
-#   ),
-#   statistic = "mad",
-#   fmt = 2
-# )
+# Print the summary of the model to inspect the results
+print(summary(aerial_priority_model))
+
+# Optional: Plot the effects to visualize the model results
+plot(aerial_priority_model)
+
+prior_summary(aerial_priority_model)
+
 ```
@@
 
-# pp_check(first_model) +
-#   theme_classic() +
-#   theme(legend.position = "bottom")
-# 
-# posterior_vs_prior(first_model) +
-#   theme_minimal() +
-#   scale_color_brewer(palette = "Set1") +
-#   theme(legend.position = "bottom") +
-#   coord_flip()
+pp_check(aerial_priority_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(aerial_priority_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
 ```
@@
 
-# plot(first_model, "trace")
-# 
-# plot(first_model, "rhat")
+plot(aerial_priority_model, "trace")
+
+plot(aerial_priority_model, "rhat")
 ```

### 2024-04-17 scripts/04-model.R

@@ -10,6 +10,8 @@
 library(rstanarm)  # Load the rstanarm package for Bayesian modeling
 library(arrow)     # Load the arrow package to read Parquet files
 library(dplyr)
+library(ggplot2)
+library(modelsummary)
 
 #### Read data ####
 cleaned_aerial_priority <- read_parquet("data/analysis_data/cleaned_aerial_priority.parquet")
@@ -36,6 +38,21 @@ print(summary(aerial_priority_model))
 # Optional: Plot the effects to visualize the model results
 plot(aerial_priority_model)
 
+prior_summary(aerial_priority_model)
+
+pp_check(aerial_priority_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(aerial_priority_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+
+plot(aerial_priority_model, "trace")
+
+plot(aerial_priority_model, "rhat")
 
 #### Save model ####
 saveRDS(

### 2024-04-17 scripts/00-simulate_data.R
complete simlulation

@@ -1,24 +1,29 @@
 #### Preamble ####
-# Purpose: Simulates an analysis dataset about Pokemon level and weakness against fire
+# Purpose: Simulates an analysis dataset about the aerial bombing campaigns against Germany
 # Author: Yunzhao Li
-# Date: 26 March 2024
+# Date: 16 April 2024
 # Contact: yunzhao.li@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: -
-# Any other information needed? -
+# Pre-requisites: None
+
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(janitor)
 
 #### Simulate data ####
-data <- 
-  tibble(
-    level = rnorm(n = 1000, mean = 100, sd = 10) |> floor(),
-    weakness = sample(x = c("fire", "not fire"), size = 1000, replace = TRUE)
+set.seed(23)
+
+simulated_aerial_data <- tibble(
+    tgt_priority_explanation = factor(sample(c('target of last resort', 'target of opportunity', 'primary target'), 1000, replace = TRUE), levels = c('target of last resort', 'target of opportunity', 'primary target')),
+    tgt_industry = sample(c('unidentified targets', 'synthetic oil refineries'), 1000, replace = TRUE),
+    country_flying_mission = sample(c('usa', 'great britain','others'), 1000, replace = TRUE),
+    total_tons = sample(1:40, 1000, replace = TRUE),
+    ac_attacking = sample(1:20, 1000, replace = TRUE)
   )
 
-
+head(simulated_aerial_data)
 
 
 

### 2024-04-17 scripts/04-model.R
move model plot to paper.qmd

@@ -10,8 +10,6 @@
 library(rstanarm)  # Load the rstanarm package for Bayesian modeling
 library(arrow)     # Load the arrow package to read Parquet files
 library(dplyr)
-library(ggplot2)
-library(modelsummary)
 
 #### Read data ####
 cleaned_aerial_priority <- read_parquet("data/analysis_data/cleaned_aerial_priority.parquet")
@@ -22,6 +20,17 @@ cleaned_aerial_priority <- read_parquet("data/analysis_data/cleaned_aerial_prior
 set.seed(302)
 sampled_data <- cleaned_aerial_priority %>%
   sample_n(1000)
+
+# Ensure the response is an ordered factor
+sampled_data$tgt_priority_explanation <- factor(
+  sampled_data$tgt_priority_explanation,
+  levels = c("target of last resort", "target of opportunity", "secondary target", "primary target"),
+  ordered = TRUE
+)
+
+# Convert categorical predictors to factors
+sampled_data$tgt_industry <- factor(sampled_data$tgt_industry)
+sampled_data$country_flying_mission <- factor(sampled_data$country_flying_mission)
 
 # Build a Bayesian ordered logistic regression model using stan_polr
 aerial_priority_model <- stan_polr(
@@ -38,21 +47,6 @@ print(summary(aerial_priority_model))
 # Optional: Plot the effects to visualize the model results
 plot(aerial_priority_model)
 
-prior_summary(aerial_priority_model)
-
-pp_check(aerial_priority_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(aerial_priority_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-
-plot(aerial_priority_model, "trace")
-
-plot(aerial_priority_model, "rhat")
 
 #### Save model ####
 saveRDS(

### 2024-04-17 paper/paper.qmd
find a bug in clean scripts, fix it and modify the sample number to 5000

@@
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+Target selection in WWII aerial campaigns was a crucial aspect that had far-reaching implications for the war’s outcome.
+This paper aims to dissect the multi-faceted considerations behind target prioritization using Bayesian statistical modeling, providing insights into historical strategies as well as methodological implications for contemporary analysis.
+We use @citeR and @rohan.
 
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+The data for this study was meticulously curated from declassified military records, comprising numerous raids, their targets, and associated strategic variables.
 
@@
 # Random sampling if needed
-set.seed(302)
-sampled_data <- cleaned_aerial_priority %>%
-  sample_n(3000)
+set.seed(131)
+sampled_aerial_data <- cleaned_aerial_priority %>%
+  sample_n(5000)
 
@@
 
-Talk more about it.
+## Variable
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+Our analysis focuses on the following variables: target priority, target industry, country of the mission's origin, total tons of bombs dropped, and the number of aircraft partaking in the mission.
 
@@
 ```{r}
-
-# analysis_data |> 
+#| fig-cap: Relationship between wing length and width
+#| echo: false
+#| warning: false
+#| message: false
+# cleaned_aerial_priority |>
 #   ggplot(aes(x = width, y = length)) +
@@
 
-Talk way more about it.
+## Justification
+
+The selected variables are integral for understanding the strategic matrix that guided target selection, enabling a thorough investigation into the strategic landscape of WWII aerial campaigns.
 
@@
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+We constructed a Bayesian ordered logistic regression model to analyze the nuanced hierarchy in target prioritization, utilizing the rstanarm package to accommodate the ordinal nature of target priority levels.
+
+Our model statistically infers the relationship between target priority and various strategic factors, providing a probabilistic assessment of their impacts.
+
+Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Our results are summarized in @tbl-modelresults.
+The analysis revealed distinct patterns in target prioritization, highlighting the role of industry type and the mission’s originating country in determining target selection, while the impact of tonnage and aircraft numbers was relatively subdued.
+@tbl-modelresults.
 
@@
 
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+# Extract model coefficients and their posterior distributions
+posterior <- as.array(aerial_priority_model)
+
+# Set the color scheme for plots
+color_scheme_set("brightblue")
+
+# Plot the credible intervals for model coefficients, focusing on categorical predictors and their impact on ordered levels of priority
+mcmc_intervals(posterior, pars = c("tgt_industryunidentified targets", "country_flying_missionusa"), prob = 0.9) +
+  labs(title = "Credible Intervals for Model Coefficients",
+       subtitle = "90% Credible Intervals showcasing the influence of categorical predictors on ordered priority levels",
+       x = "Coefficient Estimate",
+       y = "Parameters")
+
+```
+
 # Discussion
@@
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+The implications of our study stretch beyond historical curiosity, offering a lens through which modern strategic decisions can be evaluated, and the methodology refined.
 

### 2024-04-17 scripts/01-download_data.R

@@ -22,6 +22,7 @@ aerial_priority <-
 #### Save data ####
 # change the_raw_data to whatever name you assigned when you downloaded it.
 write_parquet(aerial_priority, "data/raw_data/aerial_priority.parquet") 
+write_csv(aerial_priority, "data/raw_data/aerial_priority.csv") 
 
 
 

### 2024-04-17 scripts/02-data_cleaning.R

@@ -21,9 +21,8 @@ cleaned_aerial_priority <-
   clean_names(aerial_priority) |>
   filter(
     tgt_country == "GERMANY", 
-    tgt_industry %in% c("RR INSTALLATIONS,  TRACKS,  MARSHALLING YARDS,  
-                        AND STATIONS", "SYNTHETIC OIL REFINERIES", "AIR FIELDS 
-                        AND AIRDROMES", "CITIES TOWNS AND URBAN AREAS", 
+    tgt_industry %in% c("\"RR INSTALLATIONS,  TRACKS,  MARSHALLING YARDS,  AND STATIONS\"", "SYNTHETIC OIL REFINERIES", 
+                        "AIR FIELDS AND AIRDROMES", "CITIES TOWNS AND URBAN AREAS", 
                         "UNIDENTIFIED TARGETS") ) |>
   select(tgt_priority_explanation, tgt_industry, 
          country_flying_mission, total_tons, ac_attacking) |>
@@ -34,7 +33,7 @@ cleaned_aerial_priority <-
     country_flying_mission = if_else(is.na(country_flying_mission), "others", as.character(country_flying_mission)),
     # Recode 'tgt_industry' to more general categories and convert to factor after 'tolower'
     tgt_industry = case_when(
-      tgt_industry == "rr installations,  tracks,  marshalling yards,  and stations" ~ "railway infrastructure",
+      tgt_industry == "\"rr installations,  tracks,  marshalling yards,  and stations\"" ~ "railway infrastructure",
       tgt_industry == "air fields and airdromes" ~ "air fields",
       tgt_industry == "cities towns and urban areas" ~ "urban areas",
       TRUE ~ as.character(tgt_industry)  # Keep all other industries as they are
@@ -59,4 +58,4 @@ view((cleaned_aerial_priority))
 
 #### Save data ####
 write_parquet(cleaned_aerial_priority, "data/analysis_data/cleaned_aerial_priority.parquet") 
-
+write_csv(cleaned_aerial_priority, "data/analysis_data/cleaned_aerial_priority.csv") 

### 2024-04-17 scripts/04-model.R

@@ -17,25 +17,14 @@ cleaned_aerial_priority <- read_parquet("data/analysis_data/cleaned_aerial_prior
 ### Model data ####
 
 # Random sampling if needed
-set.seed(302)
-sampled_data <- cleaned_aerial_priority %>%
-  sample_n(1000)
-
-# Ensure the response is an ordered factor
-sampled_data$tgt_priority_explanation <- factor(
-  sampled_data$tgt_priority_explanation,
-  levels = c("target of last resort", "target of opportunity", "secondary target", "primary target"),
-  ordered = TRUE
-)
-
-# Convert categorical predictors to factors
-sampled_data$tgt_industry <- factor(sampled_data$tgt_industry)
-sampled_data$country_flying_mission <- factor(sampled_data$country_flying_mission)
+set.seed(131)
+sampled_aerial_data <- cleaned_aerial_priority %>%
+  sample_n(5000)
 
 # Build a Bayesian ordered logistic regression model using stan_polr
 aerial_priority_model <- stan_polr(
   formula = tgt_priority_explanation ~ tgt_industry + country_flying_mission + total_tons + ac_attacking,
-  data = sampled_data,
+  data = sampled_aerial_data,
   method = "logistic",  # Use logistic cumulative link model
   prior = NULL,  # Use default priors to simplify the model
   prior_counts = NULL  # Use default priors for the intercepts

### 2024-04-18 paper/paper.qmd
change on variable names

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "During World War II, the strategic decisions about where and how the Allies bombed German industries played a crucial role in the Allied campaign.
+This study employs Bayesian ordered logistic regression to methodically analyze how different factors—such as the industry type, the launching country, the bomb load, and the number of aircraft—shaped these decisions.
+Focusing on the preference for targeting crucial oil refineries, the analysis sheds light on the calculated approach to disrupt Germany's war capabilities effectively.
+The insights from this research not only clarify the strategic rationale behind the Allies' bombing priorities but also enhance our understanding of their impact on the course of the war."
 format: pdf
@@
 
+#### Workspace setup ####
 library(arrow)
@@
 library(broom)
+library(gridExtra)
 ```
@@
 
-Target selection in WWII aerial campaigns was a crucial aspect that had far-reaching implications for the war’s outcome.
-This paper aims to dissect the multi-faceted considerations behind target prioritization using Bayesian statistical modeling, providing insights into historical strategies as well as methodological implications for contemporary analysis.
-We use @citeR and @rohan.
+World War II reshaped global power dynamics, with the strategic aerial bombing campaigns playing a crucial role in determining the outcome of the conflict.
+The Allied forces’ focused bombardment of German industries was pivotal, aiming to dismantle the economic backbone essential for Germany's war efforts.
+While considerable research has been conducted on the impact of these bombings, less attention has been given to the systematic selection process behind targeting specific industrial assets.
+This paper addresses this understudied aspect by exploring the intricate decision-making process that guided the Allied forces in targeting German industries.
+
+The crux of this research lies in a detailed examination of a sampled subset of over 5,000 missions from comprehensive wartime records, representing a strategic selection designed to analyze the impact of various factors on target prioritization.
+These factors include the type of industry targeted, the leading country of the mission, the volume of bombs dropped, and the scale of aircraft involvement.
+Prior literature has often provided broad overviews without delving into the interplay of these specific variables.
+By applying a Bayesian ordered logistic regression model, this study meticulously quantifies the influence of each factor, offering a clearer picture of the strategic considerations that shaped the Allied bombing strategy.
+
+Our findings indicate a deliberate emphasis on disabling critical oil refineries and other vital industrial infrastructures, which were deemed essential for sustaining the German war machine.
+The analysis underscores that missions with larger bomb payloads and more aircraft were preferentially deployed against these high-value targets.
+This targeted approach was strategic, aiming not just at destruction but at crippling Germany’s ability to sustain its military operations effectively.
+
+The significance of these insights extends beyond the historical narrative of World War II, offering lessons on the allocation of military resources and strategic target selection that are relevant to modern military strategies.
+Furthermore, this paper enriches the ongoing academic debate about the strategic efficacy and ethical considerations of aerial bombing in warfare.
 
 The remainder of this paper is structured as follows. @sec-data....
+
+[@citeR], [@R-arrow], [@R-knitr], [@R-kableExtra], [@R-modelsummary], [@R-rstanarm], [@R-tidyverse], [@R-ggplot2], [@R-bayesplot], [@R-broom], [@R-gridExtra], [@R-janitor], [@R-dplyr], [@tellingstories]
+@citeR.
 
@@
 #| label: tbl-cesdata1
-#| tbl-cap: "2022 CES (Cooperative Election Study) Data (Cultural)"
+#| tbl-cap: "Aerial Bombing missions against Germany on the main target industries in WWII "
 
@@
 
-# ces2022_1 |>
-#   head() |>
-#   kable(
-#     col.names = c("Voted For (2020)", "Age Group", "Gender", "Education", "Race", "Religion"),
-#     booktabs = TRUE
-  # )
+cleaned_aerial_priority |>
+  head() |>
+  kable(booktabs = TRUE, align = "c"
+)
 ```
@@
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: fig-industry and country by priority
+#| fig-cap: Distribution of target industry and country in mission by Priority
 #| echo: false
+
+# Update the color set based on the new requirements
+priority_colors <- c("primary target" = "#FF0000",
+                     "secondary target" = "#00BA38",
+                     "target of opportunity" = "#619CFF",
+                     "target of last resort" = "coral")
+
+# Convert country_mission to uppercase
+cleaned_aerial_priority$country_mission <- toupper(cleaned_aerial_priority$country_mission)
+
+# Create plot for tgt_industry
+plot_industry_country <- ggplot(cleaned_aerial_priority, aes(x = tgt_industry, fill = tgt_priority)) +
+  geom_bar(position = "stack") +  # Use stack position to layer the colors in one bar
+  scale_fill_manual(values = priority_colors) +
+  theme_minimal() +
+  labs(
+    title = "Distribution of Target Industry and Country in Mission by Priority",
+    x = "Target Industry",
+    y = "Count",
+    fill = "Target Priority"
+  ) +
+  facet_wrap(vars(country_mission), scales = "free_x") + # Facet by country mission
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x labels for clarity
+        legend.position = "bottom")
+print(plot_industry_country)
+```
+
+```{r}
+#| label: bomb tons and fig-aircraft attacking by priority
+#| fig-cap: Distribution of target industry and country in mission by Priority
+#| echo: false
+
+# Define the specified colors for each priority level
+priority_colors <- c("primary target" = "#FF0000",  # Red
+                     "secondary target" = "#00BA38",  # Green
+                     "target of opportunity" = "#619CFF",  # Blue
+                     "target of last resort" = "#FF7F50")  # Coral
+
+# Create a scatter plot for aircraft_attack
+plot_aircraft_attack <- ggplot(cleaned_aerial_priority, aes(x = aircraft_attack, y = tgt_priority, color = tgt_priority)) +
+  geom_jitter(width = 0.1, height = 0.1, size = 3, alpha = 0.6) +
+  scale_color_manual(values = priority_colors) +
+  theme_minimal() +
+  labs(
+    title = "Aircraft Attack Colored by Target Priority",
+    x = "Aircraft Attack",
+    y = "Target Priority",
+    color = "Target Priority"
+  ) +
+  theme(legend.position = "bottom")
+
+# Create a scatter plot for bomb_tons
+plot_bomb_tons <- ggplot(cleaned_aerial_priority, aes(x = bomb_tons, y = tgt_priority, color = tgt_priority)) +
+  geom_jitter(width = 0.1, height = 0.1, size = 3, alpha = 0.6) +
+  scale_color_manual(values = priority_colors) +
+  theme_minimal() +
+  labs(
+    title = "Bomb Tons Colored by Target Priority",
+    x = "Bomb Tons",
+    y = "Target Priority",
+    color = "Target Priority"
+  ) +
+  theme(legend.position = "bottom")
+
+print(plot_aircraft_attack)
+print(plot_bomb_tons)
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+The goal of our modelling strategy is twofold. F
+This study employs a Bayesian ordered logistic regression model to analyze the priorities assigned to different target industries during aerial bombing missions in World War II.
 
-We constructed a Bayesian ordered logistic regression model to analyze the nuanced hierarchy in target prioritization, utilizing the rstanarm package to accommodate the ordinal nature of target priority levels.
+The model integrates several predictors including the type of target industry (`tgt_industry`), the country executing the mission (`country_mission`), the tonnage of bombs dropped (`bomb_tons`), and the number of aircraft involved in the attack (`aircraft_attack`).
+
+The model uses a logistic cumulative link function, draws on a posterior sample size of 4000, and is based on a total of 5000 observations, utilizing the rstanarm package to accommodate the ordinal nature of target priority levels.
 
@@
 # Optional: Plot the effects to visualize the model results
-plot(aerial_priority_model)
 
@@
 #| warning: false
-# Extract model coefficients and their posterior distributions
+# Extract posterior arrays for the model coefficients
 posterior <- as.array(aerial_priority_model)
 
-# Set the color scheme for plots
+# Set a color scheme for the plots
 color_scheme_set("brightblue")
 
-# Plot the credible intervals for model coefficients, focusing on categorical predictors and their impact on ordered levels of priority
-mcmc_intervals(posterior, pars = c("tgt_industryunidentified targets", "country_flying_missionusa"), prob = 0.9) +
+# Plot the 90% credible intervals for all model coefficients
+# This visualizes the impact of each predictor on the ordered priority levels
+mcmc_intervals(posterior, prob = 0.9) +
   labs(title = "Credible Intervals for Model Coefficients",
-       subtitle = "90% Credible Intervals showcasing the influence of categorical predictors on ordered priority levels",
+       subtitle = "90% credible intervals demonstrating the influence of predictors on ordered priority levels",
        x = "Coefficient Estimate",
        y = "Parameters")
+
+```
+
+The Bayesian ordered logistic regression model's estimates are visualized in Figure X.
+Each point in the plot represents the posterior mean effect size of the predictor variables on the target priority ranking, while the lines indicate the 95% credible intervals.
+The estimates reveal several key insights into the Allied bombing strategy:
+
+- The variable `tgt_industrySynthetic Oil Refineries` exhibits the largest positive effect, suggesting that synthetic oil refineries were assigned the highest priority for bombing missions, in line with the strategic objective to disrupt the German war effort's fuel supply.
+- In contrast, the effects associated with `tgt_industryRailway Infrastructure` and `tgt_industryUrban Areas` are closer to zero, indicating a lower priority relative to other types of targets.
+This aligns with a strategy that placed less emphasis on disrupting transportation and civilian structures.
+- Regarding the country of mission execution, `country_missionusa` shows a significant positive effect, reflecting the United States' prominent role in the strategic bombing campaign against Germany.
+- The effects of `bomb_tons` and `aircraft_attack` are positive, suggesting that missions with greater bomb tonnage and more aircraft tend to have a higher target priority, possibly reflecting the allocation of resources to strategically important missions.
+
+These findings underscore the strategic considerations that guided the Allies' targeting decisions during World War II, highlighting the emphasis on industrial targets critical to the German war machine.
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+# Plot posterior distributions for selected parameters that influence priority levels
+mcmc_areas(posterior, pars = c("tgt_industryunidentified targets", "country_missionusa")) +
+  labs(title = "Posterior Distributions of Selected Parameters",
+       subtitle = "Focusing on how categorical predictors without inherent order affect the ordered target priority",
+       x = "Parameter Value",
+       y = "Density")
 

### 2024-04-18 scripts/02-data_cleaning.R

@@ -24,13 +24,13 @@ cleaned_aerial_priority <-
     tgt_industry %in% c("\"RR INSTALLATIONS,  TRACKS,  MARSHALLING YARDS,  AND STATIONS\"", "SYNTHETIC OIL REFINERIES", 
                         "AIR FIELDS AND AIRDROMES", "CITIES TOWNS AND URBAN AREAS", 
                         "UNIDENTIFIED TARGETS") ) |>
-  select(tgt_priority_explanation, tgt_industry, 
-         country_flying_mission, total_tons, ac_attacking) |>
+  select(tgt_priority = tgt_priority_explanation, tgt_industry, 
+         country_mission = country_flying_mission, bomb_tons = total_tons, aircraft_attack = ac_attacking) |>
   mutate(
     # Convert all character data to lowercase before any other operation
     across(where(is.character), tolower),
-    # Replace NA with "others" in 'country_flying_mission' and make sure it's a character
-    country_flying_mission = if_else(is.na(country_flying_mission), "others", as.character(country_flying_mission)),
+    # Replace NA with "others" in 'country_mission' and make sure it's a character
+    country_mission = if_else(is.na(country_mission), "others", as.character(country_mission)),
     # Recode 'tgt_industry' to more general categories and convert to factor after 'tolower'
     tgt_industry = case_when(
       tgt_industry == "\"rr installations,  tracks,  marshalling yards,  and stations\"" ~ "railway infrastructure",
@@ -39,20 +39,20 @@ cleaned_aerial_priority <-
       TRUE ~ as.character(tgt_industry)  # Keep all other industries as they are
     )
   ) %>%
-  # Now convert 'country_flying_mission' and 'tgt_industry' to factor type
+  # Now convert 'country_mission' and 'tgt_industry' to factor type
   mutate(
-    country_flying_mission = factor(country_flying_mission),
+    country_mission = factor(country_mission),
     tgt_industry = factor(tgt_industry),
-    # Convert 'tgt_priority_explanation' to an ordered factor
-    tgt_priority_explanation = factor(tgt_priority_explanation, levels = c("target of last resort", "target of opportunity", "secondary target", "primary target"), ordered = TRUE)
+    # Convert 'tgt_priority' to an ordered factor
+    tgt_priority = factor(tgt_priority, levels = c("target of last resort", "target of opportunity", "secondary target", "primary target"), ordered = TRUE)
   ) %>%
[…]

### 2024-04-18 scripts/03-test_data.R

@@ -17,39 +17,39 @@ library(arrow)
 data <- read_parquet("data/analysis_data/cleaned_aerial_priority.parquet")
 
 # Check for correct columns
-if(!all(c("tgt_priority_explanation", "tgt_industry", "country_flying_mission", "total_tons", "ac_attacking") %in% names(data))) {
+if(!all(c("tgt_priority", "tgt_industry", "country_mission", "bomb_tons", "aircraft_attack") %in% names(data))) {
   stop("Data frame does not have the correct columns.")
 }
 
 # Check for correct types
-if(!is.factor(data$tgt_priority_explanation)) {
-  stop("tgt_priority_explanation is not a factor.")
+if(!is.factor(data$tgt_priority)) {
+  stop("tgt_priority is not a factor.")
 }
 if(!is.factor(data$tgt_industry)) {
   stop("tgt_industry is not a factor.")
 }
-if(!is.factor(data$country_flying_mission)) {
-  stop("country_flying_mission is not a factor.")
+if(!is.factor(data$country_mission)) {
+  stop("country_mission is not a factor.")
 }
-if(!is.numeric(data$total_tons)) {
-  stop("total_tons is not numeric.")
+if(!is.numeric(data$bomb_tons)) {
+  stop("bomb_tons is not numeric.")
 }
-if(!is.numeric(data$ac_attacking)) {
-  stop("ac_attacking is not an numeric.")
+if(!is.numeric(data$aircraft_attack)) {
+  stop("aircraft_attack is not an numeric.")
 }
 
 # Check for expected levels in factors
 expected_levels_priority <- c("target of last resort", "target of opportunity",  "secondary target", "primary target")
-if(!all(expected_levels_priority %in% levels(data$tgt_priority_explanation))) {
-  stop("tgt_priority_explanation does not have the expected levels.")
+if(!all(expected_levels_priority %in% levels(data$tgt_priority))) {
+  stop("tgt_priority does not have the expected levels.")
 }
 
 # Check numeric variables for expected range
-if(any(data$total_tons < 0)) {
-  stop("total_tons contains negative values.")
+if(any(data$bomb_tons < 0)) {
+  stop("bomb_tons contains negative values.")
 }
-if(any(data$ac_attacking < 0)) {
-  stop("ac_attacking contains negative values.")
+if(any(data$aircraft_attack < 0)) {
+  stop("aircraft_attack contains negative values.")
 }
 
 # Check for missing values

### 2024-04-18 scripts/04-model.R

@@ -23,7 +23,7 @@ sampled_aerial_data <- cleaned_aerial_priority %>%
 
 # Build a Bayesian ordered logistic regression model using stan_polr
 aerial_priority_model <- stan_polr(
-  formula = tgt_priority_explanation ~ tgt_industry + country_flying_mission + total_tons + ac_attacking,
+  formula = tgt_priority ~ tgt_industry + country_mission + bomb_tons + aircraft_attack,
   data = sampled_aerial_data,
   method = "logistic",  # Use logistic cumulative link model
   prior = NULL,  # Use default priors to simplify the model

### 2024-04-18 paper/paper.qmd
add intro, result, discussion

@@
 library(knitr)
-library(kableExtra)
-library(modelsummary)
 library(rstanarm)
@@
 library(bayesplot)
-library(broom)
-library(gridExtra)
 ```
@@
 
-The remainder of this paper is structured as follows. @sec-data....
+The paper is organized to provide a clear and detailed examination of the strategic target prioritization during World War II aerial campaigns.
+Following the introduction in @sec-intro, @sec-data outlines the data employed in the study, describing the sources of historical military data, the variables selected for analysis, and the rationale behind these choices.
+@sec-result presents the findings from the Bayesian ordered logistic regression model, detailing how different factors such as target industry and mission country influenced the prioritization of targets.
+@sec-discussion delves deeper into these results, discussing the strategic implications of the findings, the limitations of the current study, and suggesting avenues for future research to expand upon the insights gained.
 
-[@citeR], [@R-arrow], [@R-knitr], [@R-kableExtra], [@R-modelsummary], [@R-rstanarm], [@R-tidyverse], [@R-ggplot2], [@R-bayesplot], [@R-broom], [@R-gridExtra], [@R-janitor], [@R-dplyr], [@tellingstories]
-@citeR.
+[@citeR], [@arrow], [@knitr], [@rstanarm], [@tidyverse], [@ggplot2], [@bayesplot], [@janitor], [@dplyr], [@tellingstories]
 
@@
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+y_i &\sim \mbox{OrderedLogistic}(\eta_i, \boldsymbol{\kappa}) \\
+\eta_i &= \beta_{\text{tgt\_industry}} \times \text{tgt\_industry}_i + \beta_{\text{country\_mission}} \times \text{country\_mission}_i \\
+&\quad + \beta_{\text{bomb\_tons}} \times \text{bomb\_tons}_i + \beta_{\text{aircraft\_attack}} \times \text{aircraft\_attack}_i \\
+\boldsymbol{\beta} &\sim \mbox{Normal}(0, 10) \text{ (default non-informative prior)} \\
+\boldsymbol{\kappa} &\sim \mbox{Normal}(0, 5) \text{ (default prior for cutpoints)}
 \end{align}
@@
 The analysis revealed distinct patterns in target prioritization, highlighting the role of industry type and the mission’s originating country in determining target selection, while the impact of tonnage and aircraft numbers was relatively subdued.
-@tbl-modelresults.
+@tbl-model_summary.
 
@@
 #| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| eval: false
 #| warning: false
@@
 print(summary(aerial_priority_model))
-
-# Optional: Plot the effects to visualize the model results
-
 prior_summary(aerial_priority_model)
@@
 ```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-model_summary
+#| tbl-cap: The model's coefficient summary
+#| warning: false
+#| message: false
+
+# Create a data frame containing the model's coefficient summary
+model_summary_df <- data.frame(
+  Parameter = c(
+    'Railway infrastructure',
+    'Synthetic oil refineries',
+    'Unidentified targets',
+    'Urban areas',
+    'Other countries',
+    'USA',
+    'Bomb',
+    'Aircraft',
+    'Intercept 1 (last resort|opportunity)',
+    'Intercept 2 (opportunity|secondary)',
+    'Intercept 3 (secondary|primary)'
+  ),
+  Mean = c(-1.4, -0.1, -3.4, -1.4, 0.8, 0.9, 0.0, 0.1, -3.7, -1.0, 0.4),
+  SD = c(0.1, 0.1, 0.1, 0.1, 0.3, 0.3, 0.0, 0.0, 0.4, 0.3, 0.3),
+  `10%` = c(-1.6, -0.2, -3.5, -1.6, 0.4, 0.5, 0.0, 0.1, -4.1, -1.4, 0.0),
+  `50%` = c(-1.4, -0.1, -3.4, -1.4, 0.8, 0.9, 0.0, 0.1, -3.7, -1.0, 0.4),
+  `90%` = c(-1.3, 0.1, -3.2, -1.3, 1.2, 1.3, 0.0, 0.1, -3.2, -0.5, 0.9)
+)
+
+# Use kable to create and style the table
+kable(model_summary_df, format = "markdown", align = 'c', col.names = c("Parameter", "Mean", "SD", "10%", "50%", "90%"))
+
+```
+
+As detailed in @tbl-model_summary, the coefficient summary quantitatively reflects the strategic emphases placed on various targets during World War II aerial bombings.
+For instance, the estimated coefficient for `Unidentified targets` is notably negative (Mean = -3.4), suggesting a strategic de-emphasis on these targets in comparison to other types.
+
+Conversely, `USA`-led missions are associated with a positive coefficient (Mean = 0.9), indicating a higher probability of such missions targeting high-priority objectives.
+This aligns with the historical context of the USA's significant role in the strategic bombing campaign.
+The coefficient for `Other countries` is marginally lower (Mean = 0.8), subtly reflecting the diverse strategic approaches among the Allied forces.
+
+The model's intercept terms serve to baseline the log-odds of the priority classifications, ranging from `Intercept 1 (last resort|opportunity)` with a mean of -3.7 to `Intercept 3 (secondary|primary)` with a mean of 0.4.
+These intercepts delineate the inherent ordering of target priority levels within the model, with higher intercepts corresponding to a higher likelihood of a target being deemed of primary importance.
+
+```{r}
+#| label: fig-model_coefficients
+#| fig-cap: The 90% credible intervals for all model coefficients
 #| eval: true
@@
 #| warning: false
+
 # Extract posterior arrays for the model coefficients
@@
 
-The Bayesian ordered logistic regression model's estimates are visualized in Figure X.
+The Bayesian ordered logistic regression model's estimates are visualized in @fig-model_coefficients.
 Each point in the plot represents the posterior mean effect size of the predictor variables on the target priority ranking, while the lines indicate the 95% credible intervals.
@@
 
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-# Plot posterior distributions for selected parameters that influence priority levels
-mcmc_areas(posterior, pars = c("tgt_industryunidentified targets", "country_missionusa")) +
-  labs(title = "Posterior Distributions of Selected Parameters",
-       subtitle = "Focusing on how categorical predictors without inherent order affect the ordered target priority",
-       x = "Parameter Value",
-       y = "Density")
-
-```
-
 # Discussion
 
-## First discussion point {#sec-first-point}
+This paper has initiated an inquiry into the labyrinth of decision-making within the Allied bombing strategy of World War II, applying a Bayesian ordered logistic regression model to discern the prioritization of targets.
+By selectively incorporating a subset of variables available in a rich dataset, the study uncovers patterns that delineate strategic imperatives from the vast array of aerial operations data.
 
-The implications of our study stretch beyond historical curiosity, offering a lens through which modern strategic decisions can be evaluated, and the methodology refined.
+## Comprehensive Understanding of Target Selection {#sec-first-point}
 
-## Second discussion point
+In this study, key variables such as target industry, country flying mission, bomb tons, and aircraft attacking were carefully selected based on their demonstrated strong correlation with target priority.
+This choice was guided by historical and strategic relevance, ensuring that the model reflects real-world considerations.
+The quantitative analysis substantiates the critical impact of these variables on strategic military decisions, revealing how different target industries were prioritized based on their role in the war effort.
+For instance, industries crucial to the enemy's war logistics, such as oil refineries, were often prioritized to cripple the enemy's ability to sustain military operations.
+This not only aligns with historical records but also provides a granular insight into the decision-making processes, illustrating the careful balancing act between achieving strategic objectives and managing resources effectively during the war.
 
-## Third discussion point
+## Strategic Implications of Variable Selection
 
-## Weaknesses and next steps
+The selection of variables was underpinned by a rigorous set of criteria that prioritized data completeness, the feasibility of clustering, and the strategic relevance of each variable.
+This methodological rigor was intended to mitigate any biases that might arise from incomplete or noisy data and to ensure that the analysis could stand up to academic and practical scrutiny.
+For example, while variables like THEATER or TGT_TYPE were initially considered due to their strategic importance, they were ultimately excluded from the final model due to data sparsity and the complexities associated with their categorization.
+This exclusion was a strategic decision aimed at enhancing the robustness and interpretability of the model, focusing on variables that offered clear, actionable insights.
+The chosen variables had well-defined, interpretable categories and were consistently recorded across the dataset, which bolstered the reliability of the analysis.
+This careful selection process ensures that the findings are grounded in solid data and reflect a true understanding of the strategic priorities that shaped Allied bombing campaigns during World War II.
 
-Weaknesses and next steps should also be included.
+## Weaknesses and Future Research Directions
+
+The study’s scope, while extensive, remains bounded by the choice of variables and the extent of the dataset.
+The absence of certain variables due to data limitations points to the potential for expanding the analytical framework.
+Additionally, the model’s fit, while adequate, leaves room for enhancement through alternative sampling techniques or integration with additional datasets.
+
+The path forward teems with potential, from utilizing geographical data to assess the collateral impact on civilian populations to examining the relationship between flight altitude and mission success rates.
+These avenues, ripe for exploration, promise to enrich the current understanding of wartime strategies and their implications.
+
+## Envisioning the Future of Historical Military Analysis
+
+Prospects for future research based on this dataset are immense.
+One could investigate whether there were unwritten standards during World War II for minimizing civilian harm, using the geographical coordinates available in the data to map bombing patterns against civilian population centers.
+Such analysis could offer new insights into the ethical boundaries of strategic warfare.
+
+Furthermore, understanding the correlation between flying altitude and success rates could shed light on tactical nuances that determined mission outcomes.
+The wealth of information contained in the dataset paves the way for such multifaceted investigations.
+
+## The Value of Strategic Insights
+
+This research underscores the analytical value of prioritization patterns, such as the focus on oil refineries, which could be extrapolated to anticipate enemy targets and inform defensive strategies.
+The prominence of American-led missions in prioritization further reflects the geopolitical dynamics of World War II, providing a statistical testament to the United States' influential role during the conflict.
 
@@
 
-# Additional data details
-
 # Model details {#sec-model-details}
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check.
+This shows a posterior prediction check, which compares the observed data (denoted by y) against the replicated data generated by the model (denoted by y_rep).
+The overlaid lines represent multiple posterior predictive distributions, providing a visual assessment of how well the model predictions align with the actual observed data across the range of predicted values.
+The close alignment between the curves indicates a good model fit, as the simulated data appears to capture the variability and central tendency of the observed data.
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior.
+This shows a strong influence of the data on the parameter estimates.
+This plot is crucial for understanding how the evidence in the data alters prior assumptions to shape the final inference drawn from the Bayesian model.
 
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+@fig-stanareyouokay-1 is a trace plot.
+It shows how the sampled values of each parameter evolve over time.
+Ideally, a well-mixed chain will resemble a 'hairy caterpillar', indicating that the sampling has explored the posterior distribution thoroughly and has likely achieved convergence.
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+This suggests that the chains for each parameter have likely converged to their respective posterior distributions.
+This is a critical aspect of ensuring the reliability of the Bayesian estimates for these parameters.
+The plot, therefore, supports the credibility of the posterior estimates derived from the model, provided that other diagnostic checks also affirm convergence.
+
+@fig-stanareyouokay-2 is a Rhat plot. It shows that the chains have converged to a common distribution, which is an indication of good mixing and reliable posterior estimates.
+
+This suggests convergence has likely been achieved, and the posterior distributions can be considered trustworthy for inference.
 
@@
 
+@fig-posterior is a graph shows the posterior distributions of the parameters from a Bayesian ordered logistic regression model.
+Each horizontal line represents the 50% credible interval, centered around the median of the posterior distribution for a given parameter, with the ends of the lines marking the 25th and 75th percentiles.
+The length of each line indicates the degree of uncertainty associated with the estimate of that parameter.
+
+The parameters include various target industries, countries of mission, and other factors like bomb tonnage and aircraft attacks.
+Notably, parameters such as tgt_industryunidentified targets exhibit a more negative median value, which might suggest a lower priority in the bombing strategy compared to other target types.
+
+```{r}
+#| label: fig-posterior
+#| fig-cap: The posterior distributions for all the parameters
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+
+# Extract the posterior distribution for all model coefficients
+posterior <- as.array(aerial_priority_model)
+
+# Set the color scheme for the plot
+color_scheme_set("brightblue")
+
+# Plot the posterior distributions for all parameters to assess their influence on priority levels
+mcmc_areas(posterior) +
+  labs(title = "Posterior Distributions of Model Parameters",
+       subtitle = "Assessing the influence of predictors on ordered target priority",
+       x = "Parameter Value",
+       y = "Density")
+
+```
+
 \newpage

### 2024-04-18 scripts/04-model.R

@@ -20,7 +20,6 @@ cleaned_aerial_priority <- read_parquet("data/analysis_data/cleaned_aerial_prior
 set.seed(131)
 sampled_aerial_data <- cleaned_aerial_priority %>%
   sample_n(5000)
-
 # Build a Bayesian ordered logistic regression model using stan_polr
 aerial_priority_model <- stan_polr(
   formula = tgt_priority ~ tgt_industry + country_mission + bomb_tons + aircraft_attack,

### 2024-04-18 paper/paper.qmd
add literature to intro

@@
 
-# Introduction
+# Introduction {#sec-intro}
 
@@
 The Allied forces’ focused bombardment of German industries was pivotal, aiming to dismantle the economic backbone essential for Germany's war efforts.
-While considerable research has been conducted on the impact of these bombings, less attention has been given to the systematic selection process behind targeting specific industrial assets.
-This paper addresses this understudied aspect by exploring the intricate decision-making process that guided the Allied forces in targeting German industries.
+While considerable research, such as Pape's analysis of strategic bombing's effectiveness [@Pape1996], has been conducted on the impact of these bombings, less attention has been given to the systematic selection process behind targeting specific industrial assets.
+This paper addresses this understudied aspect by exploring the intricate decision-making process that guided the Allied forces in targeting German industries [@Overy2013].
 
@@
 These factors include the type of industry targeted, the leading country of the mission, the volume of bombs dropped, and the scale of aircraft involvement.
-Prior literature has often provided broad overviews without delving into the interplay of these specific variables.
+Prior literature, such as studies by Grey [@Grey1999], has often provided broad overviews without delving into the interplay of these specific variables.
 By applying a Bayesian ordered logistic regression model, this study meticulously quantifies the influence of each factor, offering a clearer picture of the strategic considerations that shaped the Allied bombing strategy.
@@
 The significance of these insights extends beyond the historical narrative of World War II, offering lessons on the allocation of military resources and strategic target selection that are relevant to modern military strategies.
-Furthermore, this paper enriches the ongoing academic debate about the strategic efficacy and ethical considerations of aerial bombing in warfare.
+Furthermore, this paper enriches the ongoing academic debate about the strategic efficacy and ethical considerations of aerial bombing in warfare, as discussed in broader terms by scholars like Biddle [@Biddle2002] and Morrow [@Morrow2004].
 
@@
 Following the introduction in @sec-intro, @sec-data outlines the data employed in the study, describing the sources of historical military data, the variables selected for analysis, and the rationale behind these choices.
+@sec-model introduces the Bayesian ordered logistic regression model employed to analyze the relationships between our variables of interest, providing a statistical framework for understanding the strategic decisions behind target prioritization during World War II aerial campaigns.
 @sec-result presents the findings from the Bayesian ordered logistic regression model, detailing how different factors such as target industry and mission country influenced the prioritization of targets.
 @sec-discussion delves deeper into these results, discussing the strategic implications of the findings, the limitations of the current study, and suggesting avenues for future research to expand upon the insights gained.
+@sec-model-details shows plots for Posterior predictive check and Diagnostics and their analysis.
 
@@
 ```{r}
-#| label: fig-industry and country by priority
+#| label: fig-industry_country
 #| fig-cap: Distribution of target industry and country in mission by Priority
 #| echo: false
+#| fig.width: 8
+#| fig.height: 6
 
@@
 ```{r}
-#| label: bomb tons and fig-aircraft attacking by priority
-#| fig-cap: Distribution of target industry and country in mission by Priority
+#| label: fig_aircrafts
+#| fig-cap: Distribution of aircrafts by Priority
 #| echo: false
@@
 
+print(plot_aircraft_attack)
+```
+
+```{r}
+#| label: fig_bomb
+#| fig-cap: Distribution of bomb tons by Priority
+#| echo: false
 # Create a scatter plot for bomb_tons
@@
 
-print(plot_aircraft_attack)
 print(plot_bomb_tons)
@@
 
-# Model
+# Model {#sec-model}
 
@@
 
-# Results
+# Results {#sec-result}
 
@@
 mcmc_intervals(posterior, prob = 0.9) +
-  labs(title = "Credible Intervals for Model Coefficients",
-       subtitle = "90% credible intervals demonstrating the influence of predictors on ordered priority levels",
+  labs(title = "Model Coefficients",
+       subtitle = "90% credible intervals",
        x = "Coefficient Estimate",
-       y = "Parameters")
+       y = "Parameters")+
+  theme(
+    plot.title = element_text(hjust = 0.5),    # Center the main title
+    plot.subtitle = element_text(hjust = 0.5)  # Center the subtitle
+  )
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 #| warning: false
+#| fig.width: 8
 

### 2024-04-18 paper/paper.qmd
add literature content

@@
 
-[@citeR], [@arrow], [@knitr], [@rstanarm], [@tidyverse], [@ggplot2], [@bayesplot], [@janitor], [@dplyr], [@tellingstories]
-
 # Data {#sec-data}
 
-The data for this study was meticulously curated from declassified military records, comprising numerous raids, their targets, and associated strategic variables.
+The dataset used in this study was sourced from [Data World](https://data.world/datamil/world-war-ii-thor-data), which hosts comprehensive records from the Theater History of Operations (THOR) dataset, documenting aerial bombings during World War II.
+Originally consisting of approximately 178,282 records, the dataset underwent significant preprocessing to align with the specific focus of this research.
+The initial step involved filtering out records where the target location was not Germany, reducing the dataset to 64,948 entries.
+These records form the basis of the analysis, having been retained for detailed examination and modeling of strategic bombing patterns and their impacts.
+
+The data for this study was systematically downloaded, cleaned, analyzed, modeled and visualized using R [@citeR], a comprehensive statistical programming language.
+The following packages were used for this study。
+
+- **`tidyverse`** [@tidyverse]: To streamline the process of data manipulation and visualization.
+- **`ggplot2`** [@ggplot2]: Used for its powerful and flexible capabilities in creating various types of visualizations tailored to the needs of this study.
+- **`dplyr`** [@dplyr]: Employed for its intuitive functions to transform and summarize the complex data sets effectively.
+- **`bayesplot`** [@bayesplot]: Utilized for creating graphical posterior predictive checks and diagnostic plots.
+- **`rstanarm`** [@rstanarm]: Facilitated the implementation of Bayesian models, providing a straightforward way to fit regression models using Stan.
+- **`janitor`** [@janitor]: Making it simpler to handle the raw data by cleaning variable names and simplifying data structures.
+- **`arrow`** [@arrow]: Used for efficiently reading and writing large datasets, enhancing data handling capabilities.
+- **`knitr`** [@knitr]: Employed to dynamically generate reports which integrate R code with its outputs, allowing for seamless inclusion of plots and analysis results in the final document.
+- **_Telling Stories with Data_** [@tellingstories]: This book was referenced for its code and methodologies in presenting data and statistical information.
 
@@
 #| echo: false
-#| label: tbl-cesdata1
+#| label: tbl-aerial_preview
 #| tbl-cap: "Aerial Bombing missions against Germany on the main target industries in WWII "
@@
 ```
+@tbl-aerial_preview presents the first six rows from the cleansed dataset, focusing on aerial bombing missions conducted by the Allies against German industries during WWII.
+
+## Variable
+
+Our analysis focuses on the following variables, with a specific focus on `target_priority` as the dependent variable:
+
+- `target_priority`: The assigned importance level of the mission's target, serving as the dependent variable in our analysis. The categories include:
+  - `Primary target`: Highest priority targets critical to enemy's war-sustaining capabilities.
+  - `Secondary target`: Important targets with significant, but not critical, impact.
+  - `Target of opportunity`: Targets engaged opportunistically without prior planning.
+  - `Target of last resort`: Targets chosen as a fallback when preferred options are not available.
+
+- `target_industry`: The sector of infrastructure targeted, with the following possible values:
+  - `Airfields`: Targeting enemy airstrips and aircraft facilities.
+  - `Railway infrastructure`: Disrupting transportation lines and logistics.
+  - `Synthetic oil refineries`: Striking at the heart of enemy fuel production.
+  - `Unidentified targets`: Engaging targets that could not be specified.
+  - `Urban areas`: Targeting urban centers with the potential to impact enemy morale or logistics.
+
+- `country_mission`: The nation from which the mission originated, which can include:
+  - `USA`: Missions flown by the United States.
+  - `Great Britain`: Missions flown by the United Kingdom.
+  - `Others`: Missions flown by other Allied nations.
+
+- `bomb_tons`: The total weight of bombs dropped, reflecting the scale of the attack, with measures ranging from less than a ton to several hundred tons.
+
+- `aircraft_attack`: The number of aircraft participating in the mission, a reflection of the committed resources and operational scale, ranging from single aircraft to entire squadrons.
+
+Detailed information about these variables and the data structure is presented in @tbl-aerial_preview, which outlines the first few records from the processed dataset.
 
@@
   facet_wrap(vars(country_mission), scales = "free_x") + # Facet by country mission
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x labels for clarity
-        legend.position = "bottom")
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x labels for clarity
+    legend.position = "bottom",
+    plot.title = element_text(hjust = 0.5)  # Center the title
+  )
 print(plot_industry_country)
@@
 
+@fig-industry_country provides a comprehensive view of the processed data, showcasing the distribution of aerial bombardments across different industrial sectors targeted by the Allies during World War II, with a particular focus on those aimed at German industries.
+The stacked bar chart breaks down the count of missions by the leading country—Great Britain, USA, and others—and prioritizes the targets into four categories: primary target, secondary target, target of opportunity, and target of last resort.
+
+From the visualization, we can discern that airfields and urban areas were frequently targeted, but with varying levels of priority depending on the mission's country of origin.
+The significant height of bars in categories such as synthetic oil refineries and railway infrastructure under the USA banner indicates a strategic emphasis on crippling Germany's logistic and production capabilities, aligning with the Allies' broader objectives of disrupting the war-sustaining resources of the Axis power.
+
 ```{r}
-#| label: fig_aircrafts
+#| label: fig-aircrafts
 #| fig-cap: Distribution of aircrafts by Priority
@@
 
+@fig-aircrafts depicts a distribution of aircraft attacks during World War II, colored by the priority of the target they were assigned to hit.
+The data points, each representing a specific mission, are spread across four categories of target priority: primary target, secondary target, target of opportunity, and target of last resort.
+The horizontal axis shows the number of aircraft involved in each attack, offering a visual correlation between the scale of the attack and the importance of the target.
+It’s clear from the clustering of data points that primary targets often saw a higher concentration of aircraft, whereas targets of last resort were engaged with fewer aircraft, indicating a strategic allocation of aerial resources based on the priority of the target.
+
 ```{r}
-#| label: fig_bomb
+#| label: fig-bomb
 #| fig-cap: Distribution of bomb tons by Priority
@@
 print(plot_bomb_tons)
-
 ```
 
-## Variable
-
-Our analysis focuses on the following variables: target priority, target industry, country of the mission's origin, total tons of bombs dropped, and the number of aircraft partaking in the mission.
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-# cleaned_aerial_priority <- read_parquet("data/analysis_data/cleaned_aerial_priority.parquet")
-# head(cleaned_aerial_priority)
-```
-
-```{r}
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-# cleaned_aerial_priority |>
-#   ggplot(aes(x = width, y = length)) +
-#   geom_point(alpha = 0.8) +
-#   theme_minimal() +
-#   labs(x = "Wing width (mm)",
-#        y = "Wing length (mm)")
-```
+@fig-bomb visualizes the weight of bombs dropped on various targets, categorized by the priority level of the mission.
+The volume of ordinance delivered is marked along the horizontal axis, indicating the intensity of each mission.
+Data points are color-coded to represent the different priority levels: from targets of last resort, which saw the lightest bombardment, up to primary targets, which typically experienced the heaviest bombings.
+This spread suggests that higher-priority targets were often subjected to more intensive bombing campaigns, a strategic choice likely reflecting their importance to the war effort.
+The distribution illustrates the heavy investment in munitions for high-priority targets, reinforcing the critical nature of these missions.
 
@@
 
-The selected variables are integral for understanding the strategic matrix that guided target selection, enabling a thorough investigation into the strategic landscape of WWII aerial campaigns.
+The variables chosen for this study were carefully selected based on their strategic significance during World War II, as documented in the THOR dataset.
+Each variable offers insights into different aspects of the aerial bombing campaigns:
+
+- `**Target Industry (TGT_INDUSTRY)**`: Identified based on the strategic value, targeting industries critical to the war effort, such as oil refineries and transportation networks.
+- `**Country of Mission (COUNTRY_FLYING_MISSION)**`: Considered to analyze differences in target prioritization across the Allied nations.
+- `**Total Tons of Bombs (TOTAL_TONS)**`: Used to gauge the intensity and importance assigned to each mission.
+- `**Aircraft Attack (AC_ATTACKING)**`: Reflected the scale of the mission and was indicative of the level of commitment to the target.
+
+Variables such as THEATER, TGT_TYPE, and MSN_TYPE were not included due to the presence of extensive missing values or the complexity of their classifications, which could complicate the analysis.
+Similarly, variables like TOTAL_LBS, TIME_OVER_TARGET, AC_LOST, and AC_DAMAGED were omitted to keep the model focused and interpretable.
+
+To streamline the modeling process and enhance the clarity of the analysis, non-German targets were excluded from the original dataset of approximately 178,282 records.
+This data cleaning step resulted in a more focused dataset, comprising 64,948 entries, which facilitated a more efficient and targeted modeling approach.
+This pre-processing not only improved the manageability of the data but also honed the study's examination of the bombing strategies against Germany, offering a clear view of the Allied prioritization and tactical decisions.
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Let $y_i$ be the ordered categorical variable representing the priority level of the target for the $i$-th bombing mission. The predictors in the model include:
+
+- $\beta_1$: The coefficient for the `target_industry`, which indicates the type of industry targeted, such as oil refineries or transportation networks.
+It is a categorical variable with the following categories:
+  - `Airfields`
+  - `Railway infrastructure`
+  - `Synthetic oil refineries`
+  - `Unidentified targets`
+  - `Urban areas`
+
+- $\beta_2$: The coefficient for the `country_mission` variable, representing the country that carried out the mission. The possible values are `USA`, `Great Britain`, and `Others`.
+
+- $\beta_3$: The coefficient for the `bomb_tons`, which is a continuous variable measuring the total tonnage of bombs dropped during the mission.
+
+- $\beta_4$: The coefficient for the `aircraft_attack`, which is a count variable reflecting the number of aircraft participating in the mission.
+
+Each coefficient $\beta_j$ corresponds to the effect of the $j$-th predictor on the log-odds of the mission having a higher target priority.
+
+- $\eta_i$: The linear predictor or log-odds for the $i$-th observation. It is a combination of the intercept and coefficients multiplied by the predictor variables.
+
+- $\kappa$: The set of thresholds (or cutpoints) that define the boundaries between the ordered categories of the dependent variable.
+In the ordered logistic regression model, these thresholds determine the ranges of $\eta_i$ values that correspond to each category of the target priority.
+The model estimates separate $\kappa$ values for each boundary between the ordered categories.
 
@@
 
-The selection of variables was underpinned by a rigorous set of criteria that prioritized data completeness, the feasibility of clustering, and the strategic relevance of each variable.
-This methodological rigor was intended to mitigate any biases that might arise from incomplete or noisy data and to ensure that the analysis could stand up to academic and practical scrutiny.
-For example, while variables like THEATER or TGT_TYPE were initially considered due to their strategic importance, they were ultimately excluded from the final model due to data sparsity and the complexities associated with their categorization.
-This exclusion was a strategic decision aimed at enhancing the robustness and interpretability of the model, focusing on variables that offered clear, actionable insights.
-The chosen variables had well-defined, interpretable categories and were consistently recorded across the dataset, which bolstered the reliability of the analysis.
-This careful selection process ensures that the findings are grounded in solid data and reflect a true understanding of the strategic priorities that shaped Allied bombing campaigns during World War II.
+The selection of variables for this analysis was carefully orchestrated to capture the most salient elements of the strategic bombing campaigns, aligning with historical accounts and operational records.
+In particular, the emphasis on target industry and mission origins provides novel insights into the resource allocation and strategic planning of the Allied forces.
+By scrutinizing these variables, this study sheds light on the underlying strategic motives, revealing a pattern of prioritization that favored crippling the enemy's production capacity over other targets.
+
+While the exclusion of certain variables, such as THEATER and TGT_TYPE, was a deliberate decision to ensure data integrity, it also opens up avenues for future research.
+Subsequent studies could explore how different theaters of war might have diverged in their strategic approach to bombing campaigns, or how specific target types contributed to the overall war effort.
+These aspects, while beyond the scope of the current analysis, suggest a rich tapestry of strategic considerations that could be further unraveled.
 
@@
 
-The study’s scope, while extensive, remains bounded by the choice of variables and the extent of the dataset.
-The absence of certain variables due to data limitations points to the potential for expanding the analytical framework.
-Additionally, the model’s fit, while adequate, leaves room for enhancement through alternative sampling techniques or integration with additional datasets.
+The scope of this study, while comprehensive, is constrained by the variables selected and the overall dataset size.
+The omission of variables such as THEATER and TGT_TYPE, although necessary to maintain data quality, limits the depth of strategic analysis possible.
+Future studies could benefit from incorporating these and other variables, such as TIME_OVER_TARGET and AC_LOST, to provide a fuller picture of the strategic complexities of World War II aerial campaigns.
 
-The path forward teems with potential, from utilizing geographical data to assess the collateral impact on civilian populations to examining the relationship between flight altitude and mission success rates.
-These avenues, ripe for exploration, promise to enrich the current understanding of wartime strategies and their implications.
+Moreover, while the model provides a solid foundation, its predictive accuracy could be improved through more sophisticated sampling methods or by integrating additional datasets that offer broader temporal and geographic coverage.
+For instance, expanding the dataset to include more varied mission types and broader operational theaters could offer new insights into the adaptive strategies employed by the Allies over the course of the war.
+
+Looking ahead, there is significant potential to delve deeper into the effects of bombing strategies on civilian populations by integrating geographical data.
+This could help in understanding the broader humanitarian impacts of strategic bombing.
+Additionally, exploring the relationship between flight altitude and mission success could yield valuable insights into the tactical decisions made during these missions.
+This line of inquiry could benefit from the application of advanced statistical techniques or machine learning models to uncover patterns not readily visible through traditional methods.
+
+Each of these directions not only promises to expand the current understanding of wartime strategies but also contributes to the broader discourse on the ethical and strategic implications of aerial warfare both historically and in contemporary contexts.
 

### 2024-04-18 paper/paper.qmd
use style to modify

@@
   head() |>
-  kable(booktabs = TRUE, align = "c"
-)
+  kable(booktabs = TRUE, align = "c")
 ```
@@
 # Update the color set based on the new requirements
-priority_colors <- c("primary target" = "#FF0000",
+priority_colors <- c(
+  "primary target" = "#FF0000",
   "secondary target" = "#00BA38",
   "target of opportunity" = "#619CFF",
-                     "target of last resort" = "coral")
+  "target of last resort" = "coral"
+)
 
@@
 # Define the specified colors for each priority level
-priority_colors <- c("primary target" = "#FF0000",  # Red
+priority_colors <- c(
+  "primary target" = "#FF0000", # Red
   "secondary target" = "#00BA38", # Green
   "target of opportunity" = "#619CFF", # Blue
-                     "target of last resort" = "#FF7F50")  # Coral
+  "target of last resort" = "#FF7F50"
+) # Coral
 
@@
 
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
 # Results {#sec-result}
@@
 prior_summary(aerial_priority_model)
-
 ```
@@
   Parameter = c(
-    'Railway infrastructure',
-    'Synthetic oil refineries',
-    'Unidentified targets',
-    'Urban areas',
-    'Other countries',
-    'USA',
-    'Bomb',
-    'Aircraft',
-    'Intercept 1 (last resort|opportunity)',
-    'Intercept 2 (opportunity|secondary)',
-    'Intercept 3 (secondary|primary)'
+    "Railway infrastructure",
+    "Synthetic oil refineries",
+    "Unidentified targets",
+    "Urban areas",
+    "Other countries",
+    "USA",
+    "Bomb",
+    "Aircraft",
+    "Intercept 1 (last resort|opportunity)",
+    "Intercept 2 (opportunity|secondary)",
+    "Intercept 3 (secondary|primary)"
   ),
@@
 # Use kable to create and style the table
-kable(model_summary_df, format = "markdown", align = 'c', col.names = c("Parameter", "Mean", "SD", "10%", "50%", "90%"))
-
+kable(model_summary_df, format = "markdown", align = "c", col.names = c("Parameter", "Mean", "SD", "10%", "50%", "90%"))
 ```
@@
 mcmc_intervals(posterior, prob = 0.9) +
-  labs(title = "Model Coefficients",
+  labs(
+    title = "Model Coefficients",
     subtitle = "90% credible intervals",
     x = "Coefficient Estimate",
-       y = "Parameters")+
+    y = "Parameters"
+  ) +
   theme(
@@
   )
-
 ```
@@
 mcmc_areas(posterior) +
-  labs(title = "Posterior Distributions of Model Parameters",
+  labs(
+    title = "Posterior Distributions of Model Parameters",
     subtitle = "Assessing the influence of predictors on ordered target priority",
     x = "Parameter Value",
-       y = "Density")
-
+    y = "Density"
+  )
 ```

### 2024-04-18 scripts/00-simulate_data.R

@@ -16,15 +16,11 @@ library(janitor)
 set.seed(23)
 
 simulated_aerial_data <- tibble(
-    tgt_priority_explanation = factor(sample(c('target of last resort', 'target of opportunity', 'primary target'), 1000, replace = TRUE), levels = c('target of last resort', 'target of opportunity', 'primary target')),
-    tgt_industry = sample(c('unidentified targets', 'synthetic oil refineries'), 1000, replace = TRUE),
-    country_flying_mission = sample(c('usa', 'great britain','others'), 1000, replace = TRUE),
-    total_tons = sample(1:40, 1000, replace = TRUE),
-    ac_attacking = sample(1:20, 1000, replace = TRUE)
-  )
+  tgt_priority_explanation = factor(sample(c("target of last resort", "target of opportunity", "primary target"), 1000, replace = TRUE), levels = c("target of last resort", "target of opportunity", "primary target")),
+  tgt_industry = sample(c("unidentified targets", "synthetic oil refineries"), 1000, replace = TRUE),
+  country_flying_mission = sample(c("usa", "great britain", "others"), 1000, replace = TRUE),
+  total_tons = sample(1:40, 1000, replace = TRUE),
+  ac_attacking = sample(1:20, 1000, replace = TRUE)
+)
 
 head(simulated_aerial_data)
-
-
-
-

### 2024-04-18 scripts/01-download_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from 
-# Author: Yunzhao Li 
-# Date: 16 April 2024 
+# Purpose: Downloads and saves the data from
+# Author: Yunzhao Li
+# Date: 16 April 2024
 # Contact: yunzhao.li@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: None
@@ -21,9 +21,5 @@ aerial_priority <-
 
 #### Save data ####
 # change the_raw_data to whatever name you assigned when you downloaded it.
-write_parquet(aerial_priority, "data/raw_data/aerial_priority.parquet") 
-write_csv(aerial_priority, "data/raw_data/aerial_priority.csv") 
-
-
-
-         
+write_parquet(aerial_priority, "data/raw_data/aerial_priority.parquet")
+write_csv(aerial_priority, "data/raw_data/aerial_priority.csv")

### 2024-04-18 scripts/02-data_cleaning.R

@@ -20,12 +20,17 @@ aerial_priority <- read_parquet("data/raw_data/aerial_priority.parquet")
 cleaned_aerial_priority <-
   clean_names(aerial_priority) |>
   filter(
-    tgt_country == "GERMANY", 
-    tgt_industry %in% c("\"RR INSTALLATIONS,  TRACKS,  MARSHALLING YARDS,  AND STATIONS\"", "SYNTHETIC OIL REFINERIES", 
-                        "AIR FIELDS AND AIRDROMES", "CITIES TOWNS AND URBAN AREAS", 
-                        "UNIDENTIFIED TARGETS") ) |>
-  select(tgt_priority = tgt_priority_explanation, tgt_industry, 
-         country_mission = country_flying_mission, bomb_tons = total_tons, aircraft_attack = ac_attacking) |>
+    tgt_country == "GERMANY",
+    tgt_industry %in% c(
+      "\"RR INSTALLATIONS,  TRACKS,  MARSHALLING YARDS,  AND STATIONS\"", "SYNTHETIC OIL REFINERIES",
+      "AIR FIELDS AND AIRDROMES", "CITIES TOWNS AND URBAN AREAS",
+      "UNIDENTIFIED TARGETS"
+    )
+  ) |>
+  select(
+    tgt_priority = tgt_priority_explanation, tgt_industry,
+    country_mission = country_flying_mission, bomb_tons = total_tons, aircraft_attack = ac_attacking
+  ) |>
   mutate(
     # Convert all character data to lowercase before any other operation
     across(where(is.character), tolower),
@@ -36,7 +41,7 @@ cleaned_aerial_priority <-
       tgt_industry == "\"rr installations,  tracks,  marshalling yards,  and stations\"" ~ "railway infrastructure",
       tgt_industry == "air fields and airdromes" ~ "air fields",
       tgt_industry == "cities towns and urban areas" ~ "urban areas",
-      TRUE ~ as.character(tgt_industry)  # Keep all other industries as they are
+      TRUE ~ as.character(tgt_industry) # Keep all other industries as they are
     )
   ) %>%
   # Now convert 'country_mission' and 'tgt_industry' to factor type
@@ -57,5 +62,5 @@ cleaned_aerial_priority <-
 view((cleaned_aerial_priority))
 
 #### Save data ####
-write_parquet(cleaned_aerial_priority, "data/analysis_data/cleaned_aerial_priority.parquet") 
[…]

### 2024-04-18 scripts/03-test_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: Tests 
+# Purpose: Tests
 # Author: Yunzhao Li
-# Date: 16 April 2023 
-# Contact: yunzhao.li@mail.utoronto.ca 
+# Date: 16 April 2023
+# Contact: yunzhao.li@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: None
 
@@ -17,43 +17,43 @@ library(arrow)
 data <- read_parquet("data/analysis_data/cleaned_aerial_priority.parquet")
 
 # Check for correct columns
-if(!all(c("tgt_priority", "tgt_industry", "country_mission", "bomb_tons", "aircraft_attack") %in% names(data))) {
+if (!all(c("tgt_priority", "tgt_industry", "country_mission", "bomb_tons", "aircraft_attack") %in% names(data))) {
   stop("Data frame does not have the correct columns.")
 }
 
 # Check for correct types
-if(!is.factor(data$tgt_priority)) {
+if (!is.factor(data$tgt_priority)) {
   stop("tgt_priority is not a factor.")
 }
-if(!is.factor(data$tgt_industry)) {
+if (!is.factor(data$tgt_industry)) {
   stop("tgt_industry is not a factor.")
 }
-if(!is.factor(data$country_mission)) {
+if (!is.factor(data$country_mission)) {
   stop("country_mission is not a factor.")
 }
-if(!is.numeric(data$bomb_tons)) {
+if (!is.numeric(data$bomb_tons)) {
   stop("bomb_tons is not numeric.")
 }
-if(!is.numeric(data$aircraft_attack)) {
+if (!is.numeric(data$aircraft_attack)) {
   stop("aircraft_attack is not an numeric.")
 }
 
 # Check for expected levels in factors
-expected_levels_priority <- c("target of last resort", "target of opportunity",  "secondary target", "primary target")
-if(!all(expected_levels_priority %in% levels(data$tgt_priority))) {
+expected_levels_priority <- c("target of last resort", "target of opportunity", "secondary target", "primary target")
+if (!all(expected_levels_priority %in% levels(data$tgt_priority))) {
   stop("tgt_priority does not have the expected levels.")
 }
 
 # Check numeric variables for expected range
-if(any(data$bomb_tons < 0)) {
+if (any(data$bomb_tons < 0)) {
   stop("bomb_tons contains negative values.")
 }
-if(any(data$aircraft_attack < 0)) {
[…]

### 2024-04-18 scripts/04-model.R

@@ -7,8 +7,8 @@
 # Pre-requisites: None
 
 #### Workspace setup ####
-library(rstanarm)  # Load the rstanarm package for Bayesian modeling
-library(arrow)     # Load the arrow package to read Parquet files
+library(rstanarm) # Load the rstanarm package for Bayesian modeling
+library(arrow) # Load the arrow package to read Parquet files
 library(dplyr)
 
 #### Read data ####
@@ -24,9 +24,9 @@ sampled_aerial_data <- cleaned_aerial_priority %>%
 aerial_priority_model <- stan_polr(
   formula = tgt_priority ~ tgt_industry + country_mission + bomb_tons + aircraft_attack,
   data = sampled_aerial_data,
-  method = "logistic",  # Use logistic cumulative link model
-  prior = NULL,  # Use default priors to simplify the model
-  prior_counts = NULL  # Use default priors for the intercepts
+  method = "logistic", # Use logistic cumulative link model
+  prior = NULL, # Use default priors to simplify the model
+  prior_counts = NULL # Use default priors for the intercepts
 )
 
 # Print the summary of the model to inspect the results

### 2024-04-18 paper/paper.qmd
add measurement and estimand

@@
 
+## Estimand
+
+This study aims to estimate the strategic priorities that guided the Allied forces in their aerial bombing campaigns against German industries during World War II.
+By analyzing various factors such as the type of industry targeted, the country leading the mission, the tonnage of bombs dropped, and the number of aircraft involved, this research seeks to understand how these variables influenced the decision-making processes regarding target selection.
+The core goal is to determine the causal effect of these factors on the prioritization of bombing targets, thereby shedding light on how strategic necessities, resource availability, and tactical choices shaped the wartime operations.
+
 # Data {#sec-data}
+
+## Measurement
 

### 2024-04-18 paper/paper.qmd
add model justification to result

@@
 
+## Model Justification
 The analysis revealed distinct patterns in target prioritization, highlighting the role of industry type and the mission’s originating country in determining target selection, while the impact of tonnage and aircraft numbers was relatively subdued.

### 2024-04-18 paper/datasheet_template.qmd
update llm and finish datasheet

---
title: "Datasheet for 'Theater History of Operations (THOR) dataset'"
author: 
  - Yunzhao Li
thanks: "Code and data are available at: https://github.com/yunzhaol/aerial_bomb_priority.git."
date: today
date-format: "D MMMM YYYY"
abstract: "This datasheet provides a detailed description of a historical dataset compiled to study the strategic bombing campaigns during World War II, focusing specifically on Allied missions targeting Germany. The dataset encompasses over 60,000 records refined from a larger repository of military operations, meticulously curated to highlight missions with direct implications on strategic outcomes. It includes variables like target industry, country flying the mission, bomb tonnage, and aircraft count, each chosen for their relevance to understanding target prioritization."
format: pdf
number-sections: true
bibliography: references.bib
---

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to analyze the strategic priorities and target selection processes in the Allied aerial bombing campaigns during World War II. It fills the gap of understanding the underlying decision-making criteria that influenced the selection of industrial and urban targets in Nazi Germany.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was developed by a collaborative effort of historians and data scientists, focusing on military history and data analytics.

3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The project was funded by [datamil].

4. *Any other comments?*
    - The dataset is part of a larger effort to digitally archive and analyze historical military operations to provide insights into their implications for modern warfare.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instance represents an aerial bombing mission during World War II, specifically targeting German industries. The data includes mission details, targets, bomb tonnage, and the countries involved.

2. *How many instances are there in total (of each type, if appropriate)?*
	- The dataset for modeling consists of approximately 5,000 instances, each corresponding to a separate bombing mission.

3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a selective sample from a larger set of wartime records, specifically filtered to focus on missions targeting Germany. The sample was chosen to represent a cross-section of different mission types and target priorities, ensuring a comprehensive analysis of strategic bombing tactics.

4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consists of structured data detailing the mission date, target type, bomb tonnage, the originating country of the mission, and the outcome. This data is derived from historical mission reports and operational records.

5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Each mission instance includes labels categorizing the target priority (e.g., primary, secondary, opportunistic, last resort) based on strategic importance.

6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Some instances may lack complete details on the exact number of aircraft involved or the precise impact of the bombing, due to the limitations in the historical records available.

7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Relationships are made explicit through the targeting data, where multiple missions targeting the same industry or geographic area are linked, showing the strategic focus over time.

8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- Split into a training set (80%) and a testing set (20%) will be fine.

9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Given the historical nature of the data, some level of noise and error is inherent, such as discrepancies in mission records or incomplete documentation of outcomes.

10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is primarily self-contained, but it is supplemented by external archival resources and historical databases, which are maintained by reputable historical and governmental archives. These resources are expected to remain available and consistent over time, with no associated fees for academic use.

11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- The dataset does not contain confidential information. All data is derived from publicly available historical records.

12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- The dataset contains descriptions of wartime activities, which may be disturbing but are presented in a factual and historical context.

13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- The dataset does not identify sub-populations as it focuses solely on military missions and does not include demographic information.

14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- It is not possible to identify individuals directly from this dataset as it does not contain personal information or identifiers.

15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- The dataset does not contain sensitive information as defined above. It strictly includes operational details of military missions.

16. *Any other comments?*
	- This dataset provides a unique perspective on a pivotal aspect of World War II and is intended for academic research and educational purposes to further understand the strategic decisions of that era.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
    - Data for each instance was directly observed and recorded from historical documents and mission reports. Validation was conducted through cross-referencing multiple sources to ensure accuracy and reliability of the mission details.

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
    - Data collection involved digital archiving tools and software for extracting information from scanned documents and digital records. Validation procedures included manual checks and comparisons against established historical records to confirm the veracity of the data extracted.

3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
    - The sampling strategy was non-random and purposive, aimed at collecting data that specifically represented bombing missions over Germany during World War II. This approach ensured the focus remained on strategic target selection within the defined scope of the study.

4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
    - Data collection was conducted by academic researchers and graduate students specializing in historical data analysis. Compensation was aligned with academic research grants and institutional funding.

5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
    - The data collection took place over several years, aligning with the ongoing efforts to digitize and analyze historical military records. The creation timeframe of the data matches the period of World War II, specifically 1939-1945, ensuring that the data collection directly corresponds to the historical events being studied.

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - Ethical reviews were conducted by the hosting academic institution’s review board to ensure compliance with historical research ethics, particularly in handling war-related data. The outcomes confirmed that the research met all ethical standards for academic study.

7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
    - Data was obtained from third-party sources, primarily historical archives and digital databases that store World War II military records.

8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
    - As the data pertains to historical events and is derived from public and institutional archives, individual notification was not applicable. All data used is in the public domain or available through academic and public archives.

9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
    - Consent is not applicable as the data involves historical figures and events, with all information sourced from publicly accessible or academically permissible resources.

10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
    - Consent and revocation are not applicable to this dataset due to its historical nature and the public status of the data used.

11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - An impact analysis was not necessary given the historical and non-personal nature of the data. The use of the dataset is intended for academic and educational purposes, aligned with historical research norms.

12. *Any other comments?*
    - The dataset serves as a valuable resource for understanding the strategic dimensions of aerial warfare during World War II and adheres to all standards of historical research and data usage.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
    - Preprocessing involved standardizing data formats, verifying the accuracy of mission details, and labeling data based on target types and priority levels. This process was crucial to ensure that analyses conducted on the dataset are reliable and valid.

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
    - Both raw and processed data are preserved to allow for verification of processed results and to support future research that might require access to unmodified historical records. The data is stored securely in compliance with academic data management policies.

3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
    - The software tools used for data preprocessing, primarily R scripts and database management applications, are documented and available through the academic institution’s digital repository to ensure transparency and reproducibility of the research.

4. *Any other comments?*
    - The meticulous preprocessing and labeling of the data underscore the rigorous standards followed in handling and analyzing historical datasets.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
    - The dataset has been utilized in several academic projects and publications that analyze strategic decision-making in World War II aerial campaigns. These studies have contributed new insights into military history and strategic studies.

2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
    - Publications and research projects utilizing the dataset are cataloged in the academic institution’s library system and are accessible via the institution’s repository.

3. *What (other) tasks could the dataset be used for?*
    - Beyond the current research focus, the dataset has potential applications in comparative military analysis, educational programs on World War II, and computational models simulating wartime decision-making processes.

4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
    - Consumers of the dataset should be aware of its historical context and the limitations inherent in wartime records. Researchers are advised to consider these factors when interpreting the data and to avoid extrapolating findings beyond the appropriate historical and strategic contexts.

5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
    - The dataset is not suitable for applications outside of historical and academic research, particularly those that could lead to the misrepresentation or trivialization of World War II events. It should not be used for commercial purposes or in ways that could misconstrue the gravity of the subject matter.

6. *Any other comments?*
    - The dataset represents a critical resource for understanding a pivotal era in military history and should be used responsibly and with respect to the historical significance of the events it documents.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
    - While the dataset itself is not distributed commercially, it is available for academic and research use through collaborations with other institutions and researchers. This ensures that the dataset can be used to advance knowledge in the field of military history.

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
    - The dataset is distributed through academic channels, including scholarly databases and conference presentations. It does not have a DOI but is cataloged in the institution’s academic records.

3. *When will the dataset be distributed?*
    - The dataset is available for use following its introduction at academic conferences and its inclusion in published research articles.

4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
    - The dataset is covered under academic use policies, which restrict its use to non-commercial, educational, and research activities. Specific terms of use are detailed in the licensing agreements provided with the dataset documentation.

5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
    - No third-party IP restrictions apply to the dataset, as all data is derived from public or institutionally held records that are free from such constraints.

6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
    - No export controls or regulatory restrictions apply to the dataset. The data is historical and does not contain sensitive or regulated information.

7. *Any other comments?*
    - The distribution of the dataset is governed by ethical considerations and academic standards, ensuring its responsible use and dissemination.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
    - The dataset will be maintained by the academic institution where it was developed, with oversight by the research team responsible for its creation.

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
    - The dataset curator can be contacted through the academic institution’s department of history, via the contact information provided on the department’s webpage.

3. *Is there an erratum? If so, please provide a link or other access point.*
    - Any corrections or updates to the dataset will be documented in the erratum section of the academic repository where the dataset is stored.

4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
    - Updates to the dataset may occur as new historical documents are discovered and integrated. These updates will be handled by the research team and communicated through academic publications and updates to the repository.

5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
    - As the dataset pertains to historical events and does not involve personal data, there are no specific retention limits. However, all data is handled in accordance with historical research ethics and privacy standards.

6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
    - Older versions of the dataset will be archived and available upon request. Any changes to the dataset’s availability will be communicated via the institution’s academic channels.

7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
    - Contributions to the dataset are welcomed and can be made through academic collaboration with the research team. All contributions will be rigorously reviewed and integrated following standard academic practices to ensure their accuracy and relevance. Communication of these contributions will be managed through scholarly publications and academic presentations.

8. *Any other comments?*
    - The maintenance of the dataset is committed to upholding the highest standards of historical accuracy and research integrity, ensuring that it remains a reliable resource for understanding World War II aerial strategies.

\newpage

# References

### 2024-04-18 paper/paper.qmd
remove unnecessary words and filler phrases

@@
 date-format: long
-abstract: "During World War II, the strategic decisions about where and how the Allies bombed German industries played a crucial role in the Allied campaign.
+abstract: "During World War II, the strategic decisions about where and how the Allies bombed German industries played an essential role in the Allied campaign.
 This study employs Bayesian ordered logistic regression to methodically analyze how different factors—such as the industry type, the launching country, the bomb load, and the number of aircraft—shaped these decisions.
-Focusing on the preference for targeting crucial oil refineries, the analysis sheds light on the calculated approach to disrupt Germany's war capabilities effectively.
+Focusing on the preference for targeting essential oil refineries, the analysis sheds light on the calculated approach to disrupt Germany's war capabilities effectively.
 The insights from this research not only clarify the strategic rationale behind the Allies' bombing priorities but also enhance our understanding of their impact on the course of the war."
@@
 
-World War II reshaped global power dynamics, with the strategic aerial bombing campaigns playing a crucial role in determining the outcome of the conflict.
+World War II reshaped global power dynamics, with the strategic aerial bombing campaigns playing a essential role in determining the outcome of the conflict.
 The Allied forces’ focused bombardment of German industries was pivotal, aiming to dismantle the economic backbone essential for Germany's war efforts.
@@
 
-The crux of this research lies in a detailed examination of a sampled subset of over 5,000 missions from comprehensive wartime records, representing a strategic selection designed to analyze the impact of various factors on target prioritization.
+The crux of this research lies in a detailed examination of a sampled subset of over 5,000 missions from extensive wartime records, representing a strategic selection designed to analyze the impact of various factors on target prioritization.
 These factors include the type of industry targeted, the leading country of the mission, the volume of bombs dropped, and the scale of aircraft involvement.
@@
 @sec-result presents the findings from the Bayesian ordered logistic regression model, detailing how different factors such as target industry and mission country influenced the prioritization of targets.
-@sec-discussion delves deeper into these results, discussing the strategic implications of the findings, the limitations of the current study, and suggesting avenues for future research to expand upon the insights gained.
+@sec-discussion examines these results, discussing the strategic implications of the findings, the limitations of the current study, and suggesting avenues for future research to expand upon the insights gained.
 @sec-model-details shows plots for Posterior predictive check and Diagnostics and their analysis.
@@
 
-The dataset used in this study was sourced from [Data World](https://data.world/datamil/world-war-ii-thor-data), which hosts comprehensive records from the Theater History of Operations (THOR) dataset, documenting aerial bombings during World War II.
+The dataset used in this study was sourced from [Data World](https://data.world/datamil/world-war-ii-thor-data), which hosts extensive records from the Theater History of Operations (THOR) dataset, documenting aerial bombings during World War II.
 Originally consisting of approximately 178,282 records, the dataset underwent significant preprocessing to align with the specific focus of this research.
@@
 
-The data for this study was systematically downloaded, cleaned, analyzed, modeled and visualized using R [@citeR], a comprehensive statistical programming language.
+The data for this study was systematically downloaded, cleaned, analyzed, modeled and visualized using R [@citeR], a extensive statistical programming language.
 The following packages were used for this study。
@@
 
-@fig-industry_country provides a comprehensive view of the processed data, showcasing the distribution of aerial bombardments across different industrial sectors targeted by the Allies during World War II, with a particular focus on those aimed at German industries.
+@fig-industry_country provides a extensive view of the processed data, showcasing the distribution of aerial bombardments across different industrial sectors targeted by the Allies during World War II, with a particular focus on those aimed at German industries.
 The stacked bar chart breaks down the count of missions by the leading country—Great Britain, USA, and others—and prioritizes the targets into four categories: primary target, secondary target, target of opportunity, and target of last resort.
@@
 
-## Comprehensive Understanding of Target Selection {#sec-first-point}
+## Extensive Understanding of Target Selection {#sec-first-point}
 
@@
 The quantitative analysis substantiates the critical impact of these variables on strategic military decisions, revealing how different target industries were prioritized based on their role in the war effort.
-For instance, industries crucial to the enemy's war logistics, such as oil refineries, were often prioritized to cripple the enemy's ability to sustain military operations.
+For instance, industries essential to the enemy's war logistics, such as oil refineries, were often prioritized to cripple the enemy's ability to sustain military operations.
 This not only aligns with historical records but also provides a granular insight into the decision-making processes, illustrating the careful balancing act between achieving strategic objectives and managing resources effectively during the war.
@@
 
-The scope of this study, while comprehensive, is constrained by the variables selected and the overall dataset size.
+The scope of this study, while extensive, is constrained by the variables selected and the overall dataset size.
 The omission of variables such as THEATER and TGT_TYPE, although necessary to maintain data quality, limits the depth of strategic analysis possible.
@@
 
-Moreover, while the model provides a solid foundation, its predictive accuracy could be improved through more sophisticated sampling methods or by integrating additional datasets that offer broader temporal and geographic coverage.
+Moreover, while the model provides a solid foundation, its predictive accuracy could be improved through more advanced sampling methods or by integrating additional datasets that offer broader temporal and geographic coverage.
 For instance, expanding the dataset to include more varied mission types and broader operational theaters could offer new insights into the adaptive strategies employed by the Allies over the course of the war.
 
-Looking ahead, there is significant potential to delve deeper into the effects of bombing strategies on civilian populations by integrating geographical data.
+Looking ahead, there is significant potential to examine the effects of bombing strategies on civilian populations by integrating geographical data.
 This could help in understanding the broader humanitarian impacts of strategic bombing.
@@
 
-Furthermore, understanding the correlation between flying altitude and success rates could shed light on tactical nuances that determined mission outcomes.
+Furthermore, understanding the correlation between flying altitude and success rates could clarify tactical nuances that determined mission outcomes.
 The wealth of information contained in the dataset paves the way for such multifaceted investigations.
@@
 This shows a strong influence of the data on the parameter estimates.
-This plot is crucial for understanding how the evidence in the data alters prior assumptions to shape the final inference drawn from the Bayesian model.
+This plot is essential for understanding how the evidence in the data alters prior assumptions to shape the final inference drawn from the Bayesian model.
 
@@
 It shows how the sampled values of each parameter evolve over time.
-Ideally, a well-mixed chain will resemble a 'hairy caterpillar', indicating that the sampling has explored the posterior distribution thoroughly and has likely achieved convergence.
+Ideally, a well-mixed chain will resemble a 'hairy caterpillar', indicating that the sampling has explored the posterior distribution extensively and has likely achieved convergence.
 

### 2024-04-18 scripts/00-simulate_data.R
add comment and modify style

@@ -13,14 +13,33 @@ library(tidyverse)
 library(janitor)
 
 #### Simulate data ####
+# Set seed for reproducibility
 set.seed(23)
 
+# Create a tibble with simulated data for aerial missions
 simulated_aerial_data <- tibble(
-  tgt_priority_explanation = factor(sample(c("target of last resort", "target of opportunity", "primary target"), 1000, replace = TRUE), levels = c("target of last resort", "target of opportunity", "primary target")),
-  tgt_industry = sample(c("unidentified targets", "synthetic oil refineries"), 1000, replace = TRUE),
-  country_flying_mission = sample(c("usa", "great britain", "others"), 1000, replace = TRUE),
-  total_tons = sample(1:40, 1000, replace = TRUE),
-  ac_attacking = sample(1:20, 1000, replace = TRUE)
+  # Simulate target priority levels as a factor with ordered levels
+  tgt_priority = factor(
+    sample(c("target of last resort", "target of opportunity", "primary target"), 
+           1000, replace = TRUE), 
+    levels = c("target of last resort", "target of opportunity", "primary target")
+  ),
+  
+  # Simulate target industry types
+  tgt_industry = sample(c("unidentified targets", "synthetic oil refineries"), 
+                        1000, replace = TRUE),
+  
+  # Simulate the country executing the mission
+  country_mission = sample(c("usa", "great britain", "others"), 
+                                  1000, replace = TRUE),
+  
+  # Simulate the total tons of bombs dropped
+  bomb_tons = sample(1:40, 1000, replace = TRUE),
+  
+  # Simulate the number of aircraft involved in the attack
+  aircraft_attack = sample(1:20, 1000, replace = TRUE)
 )
 
+# Display the first few rows of the simulated data
 head(simulated_aerial_data)
+

### 2024-04-18 paper/paper.qmd
add prior distribution and center the title in fig7

@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+## Prior distributions
+
+In the Bayesian ordered logistic regression model implemented using the `rstanarm` package, default priors are applied to the model parameters to ensure robust and reliable inference.
+These priors are designed to be weakly informative, balancing the need for regularization with the flexibility to adapt to the data:
+
+- **Intercept Priors**: For the model's intercepts, a normal prior distribution is typically used with a mean of 0.
+This choice helps stabilize the location parameter without imposing too strong a belief about where it should be centered.
+
+- **Coefficient Priors**: Coefficients in the model are also assigned normal prior distributions with a mean of 0.
+The standard deviation for these priors is often set around 2.5, a value chosen to prevent overly large effects unless strongly supported by the data, thereby adding a level of regularization.
+
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm.
+We use the default priors from `rstanarm`.These priors are intended to provide a default level of smoothing and regularization to the model, making it applicable to a wide range of datasets while still being flexible enough to capture essential data-driven insights.
 
@@
 ## Model Justification
+
 The analysis revealed distinct patterns in target prioritization, highlighting the role of industry type and the mission’s originating country in determining target selection, while the impact of tonnage and aircraft numbers was relatively subdued.
@@
     y = "Density"
+  ) +
+  theme(
+    plot.title = element_text(hjust = 0.5), # Center the main title
+    plot.subtitle = element_text(hjust = 0.5) # Center the subtitle
   )

### 2024-04-18 paper/paper.qmd
polish the words, modify some styles

@@
 abstract: "During World War II, the strategic decisions about where and how the Allies bombed German industries played an essential role in the Allied campaign.
-This study employs Bayesian ordered logistic regression to methodically analyze how different factors—such as the industry type, the launching country, the bomb load, and the number of aircraft—shaped these decisions.
-Focusing on the preference for targeting essential oil refineries, the analysis sheds light on the calculated approach to disrupt Germany's war capabilities effectively.
+This study employs Bayesian ordered logistic regression to methodically analyze how different factors—such as the industry type, the launching country, the bomb load, and the number of aircraft—influenced the prioritization of targets.
+Focusing on the strategic choice to target essential oil refineries, the analysis highlights how these attacks were aimed to cripple Germany's war capabilities effectively.
 The insights from this research not only clarify the strategic rationale behind the Allies' bombing priorities but also enhance our understanding of their impact on the course of the war."
@@
 Prior literature, such as studies by Grey [@Grey1999], has often provided broad overviews without delving into the interplay of these specific variables.
-By applying a Bayesian ordered logistic regression model, this study meticulously quantifies the influence of each factor, offering a clearer picture of the strategic considerations that shaped the Allied bombing strategy.
+By applying a Bayesian ordered logistic regression model, this study effectively quantifies the influence of each factor, offering a clearer picture of the strategic considerations that shaped the Allied bombing strategy.
 
@@
 @sec-discussion examines these results, discussing the strategic implications of the findings, the limitations of the current study, and suggesting avenues for future research to expand upon the insights gained.
-@sec-model-details shows plots for Posterior predictive check and Diagnostics and their analysis.
+@sec-model-details shows plots for Posterior predictive check and Diagnostics as well as their analysis.
 
@@
 By analyzing various factors such as the type of industry targeted, the country leading the mission, the tonnage of bombs dropped, and the number of aircraft involved, this research seeks to understand how these variables influenced the decision-making processes regarding target selection.
-The core goal is to determine the causal effect of these factors on the prioritization of bombing targets, thereby shedding light on how strategic necessities, resource availability, and tactical choices shaped the wartime operations.
+The core goal is to determine the causal effect of these factors on the prioritization of bombing targets, thereby examining how strategic necessities, resource availability, and tactical choices shaped the wartime operations.
 
@@
 
-- `**Target Industry (TGT_INDUSTRY)**`: Identified based on the strategic value, targeting industries critical to the war effort, such as oil refineries and transportation networks.
-- `**Country of Mission (COUNTRY_FLYING_MISSION)**`: Considered to analyze differences in target prioritization across the Allied nations.
-- `**Total Tons of Bombs (TOTAL_TONS)**`: Used to gauge the intensity and importance assigned to each mission.
-- `**Aircraft Attack (AC_ATTACKING)**`: Reflected the scale of the mission and was indicative of the level of commitment to the target.
+- **Target Industry (`TGT_INDUSTRY`):** Identified based on the strategic value, targeting industries critical to the war effort, such as oil refineries and transportation networks.
+- **Country of Mission (`COUNTRY_FLYING_MISSION`):** Considered to analyze differences in target prioritization across the Allied nations.
+- **Total Tons of Bombs (`TOTAL_TONS`):** Used to gauge the intensity and importance assigned to each mission.
+- **Aircraft Attack (`AC_ATTACKING`):** Reflected the scale of the mission and was indicative of the level of commitment to the target.
 
-Variables such as THEATER, TGT_TYPE, and MSN_TYPE were not included due to the presence of extensive missing values or the complexity of their classifications, which could complicate the analysis.
-Similarly, variables like TOTAL_LBS, TIME_OVER_TARGET, AC_LOST, and AC_DAMAGED were omitted to keep the model focused and interpretable.
+*THEATER*, *TGT_TYPE*, and *MSN_TYPE* were not included due to the presence of extensive missing values or the complexity of their classifications, which could complicate the analysis.
+Similarly, variables like *TOTAL_LBS*, *TIME_OVER_TARGET*, *AC_LOST*, and *AC_DAMAGED* were omitted to keep the model focused and interpretable.
 

### 2024-04-18 paper/paper.qmd
final polish

@@
 
-The goal of our modelling strategy is twofold. F
 This study employs a Bayesian ordered logistic regression model to analyze the priorities assigned to different target industries during aerial bombing missions in World War II.
 
-The model integrates several predictors including the type of target industry (`tgt_industry`), the country executing the mission (`country_mission`), the tonnage of bombs dropped (`bomb_tons`), and the number of aircraft involved in the attack (`aircraft_attack`).
+The model integrates several key predictors:
+
+- Type of Target Industry: Identifies the industry sector being targeted.
+  Variable: `tgt_industry`
+
+- Country Executing the Mission: Indicates the nation responsible for carrying out the mission.
+  Variable: `country_mission`
+
+- Tonnage of Bombs Dropped: Measures the weight of bombs used in the mission.
+  Variable: `bomb_tons`
+
+- Number of Aircraft Involved in the Attack: Reflects the scale of the aerial attack.
+  Variable: `aircraft_attack`
 
@@
 
-- The variable `tgt_industrySynthetic Oil Refineries` exhibits the largest positive effect, suggesting that synthetic oil refineries were assigned the highest priority for bombing missions, in line with the strategic objective to disrupt the German war effort's fuel supply.
-- In contrast, the effects associated with `tgt_industryRailway Infrastructure` and `tgt_industryUrban Areas` are closer to zero, indicating a lower priority relative to other types of targets.
+- The variable `tgt_industry Synthetic Oil Refineries` exhibits the largest positive effect, suggesting that synthetic oil refineries were assigned the highest priority for bombing missions, in line with the strategic objective to disrupt the German war effort's fuel supply.
+- In contrast, the effects associated with `tgt_industry Railway Infrastructure` and `tgt_industry Urban Areas` are closer to zero, indicating a lower priority relative to other types of targets.
 This aligns with a strategy that placed less emphasis on disrupting transportation and civilian structures.
-- Regarding the country of mission execution, `country_missionusa` shows a significant positive effect, reflecting the United States' prominent role in the strategic bombing campaign against Germany.
+- Regarding the country of mission execution, `country_mission usa` shows a significant positive effect, reflecting the United States' prominent role in the strategic bombing campaign against Germany.
 - The effects of `bomb_tons` and `aircraft_attack` are positive, suggesting that missions with greater bomb tonnage and more aircraft tend to have a higher target priority, possibly reflecting the allocation of resources to strategically important missions.
@@
 
-This paper has initiated an inquiry into the labyrinth of decision-making within the Allied bombing strategy of World War II, applying a Bayesian ordered logistic regression model to discern the prioritization of targets.
+This paper has initiated an inquiry into the framework of decision-making within the Allied bombing strategy of World War II, applying a Bayesian ordered logistic regression model to indentify the prioritization of targets.
 By selectively incorporating a subset of variables available in a rich dataset, the study uncovers patterns that delineate strategic imperatives from the vast array of aerial operations data.
 
-## Extensive Understanding of Target Selection {#sec-first-point}
+## Extensive Understanding of Target Selection
 
-In this study, key variables such as target industry, country flying mission, bomb tons, and aircraft attacking were carefully selected based on their demonstrated strong correlation with target priority.
-This choice was guided by historical and strategic relevance, ensuring that the model reflects real-world considerations.
-The quantitative analysis substantiates the critical impact of these variables on strategic military decisions, revealing how different target industries were prioritized based on their role in the war effort.
-For instance, industries essential to the enemy's war logistics, such as oil refineries, were often prioritized to cripple the enemy's ability to sustain military operations.
-This not only aligns with historical records but also provides a granular insight into the decision-making processes, illustrating the careful balancing act between achieving strategic objectives and managing resources effectively during the war.
+This study meticulously selects key variables—target industry, country flying mission, bomb tons, and aircraft attacking—based on their strong correlation with target priority.
+Historical and strategic relevance guided this choice, ensuring the model’s alignment with real-world scenarios.
+The quantitative analysis highlights how these variables critically influence strategic military decisions.
+For example, industries crucial to the enemy's war logistics, like oil refineries, were frequently targeted to undermine the enemy’s military sustainability.
+This not only corroborates historical records but also enhances our understanding of the nuanced decision-making that guided the allocation of military resources during the war.
 
@@
 
-The selection of variables for this analysis was carefully orchestrated to capture the most salient elements of the strategic bombing campaigns, aligning with historical accounts and operational records.
-In particular, the emphasis on target industry and mission origins provides novel insights into the resource allocation and strategic planning of the Allied forces.
-By scrutinizing these variables, this study sheds light on the underlying strategic motives, revealing a pattern of prioritization that favored crippling the enemy's production capacity over other targets.
-
-While the exclusion of certain variables, such as THEATER and TGT_TYPE, was a deliberate decision to ensure data integrity, it also opens up avenues for future research.
-Subsequent studies could explore how different theaters of war might have diverged in their strategic approach to bombing campaigns, or how specific target types contributed to the overall war effort.
-These aspects, while beyond the scope of the current analysis, suggest a rich tapestry of strategic considerations that could be further unraveled.
+In focusing on the strategic implications of variable selection, this analysis aligns with documented historical strategies and operational records.
+Emphasizing target industry and mission origins provides fresh perspectives on resource allocation and strategic planning by the Allied forces.
+The study reveals a consistent strategic pattern: prioritizing the disruption of the enemy’s production capabilities.
+Although certain variables such as *THEATER* and *TGT_TYPE* were excluded to maintain data integrity, this decision highlights areas for future research.
+Future studies might investigate the variances in strategic approaches across different theaters of war or the specific contributions of various target types to the war effort.
+These potential research paths underscore the complex fabric of strategic decisions that warrant further exploration.
 
@@
 The scope of this study, while extensive, is constrained by the variables selected and the overall dataset size.
-The omission of variables such as THEATER and TGT_TYPE, although necessary to maintain data quality, limits the depth of strategic analysis possible.
-Future studies could benefit from incorporating these and other variables, such as TIME_OVER_TARGET and AC_LOST, to provide a fuller picture of the strategic complexities of World War II aerial campaigns.
+The omission of variables such as *THEATER* and *TGT_TYPE*, although necessary to maintain data quality, limits the depth of strategic analysis possible.
+Future studies could benefit from incorporating these and other variables, such as *TIME_OVER_TARGET* and *AC_LOST*, to provide a fuller picture of the strategic complexities of World War II aerial campaigns.
 
@@
 The parameters include various target industries, countries of mission, and other factors like bomb tonnage and aircraft attacks.
-Notably, parameters such as tgt_industryunidentified targets exhibit a more negative median value, which might suggest a lower priority in the bombing strategy compared to other target types.
+Notably, parameters such as *tgt_industry unidentified targets* exhibit a more negative median value, which might suggest a lower priority in the bombing strategy compared to other target types.
 

### 2024-04-18 paper/paper.qmd
modify vague sentences

@@
 Prospects for future research based on this dataset are immense.
-One could investigate whether there were unwritten standards during World War II for minimizing civilian harm, using the geographical coordinates available in the data to map bombing patterns against civilian population centers.
+One could investigate whether there were implicit humanitarian norms upheld by nations during World War II for minimizing civilian harm, using the geographical coordinates available in the data to map bombing patterns against civilian population centers.
 Such analysis could offer new insights into the ethical boundaries of strategic warfare.
@@
 In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check.
-This shows a posterior prediction check, which compares the observed data (denoted by y) against the replicated data generated by the model (denoted by y_rep).
+This shows a posterior prediction check, which compares the observed data *y* against the replicated data *y_rep* generated by the model.
 The overlaid lines represent multiple posterior predictive distributions, providing a visual assessment of how well the model predictions align with the actual observed data across the range of predicted values.

### 2024-04-19 paper/paper.qmd
modify the title

@@
 ---
-title: "Bayesian Insights into Aerial Bombing Strategies: An Ordered Logistic Regression Analysis of WWII Target Prioritization Against Germany"
+title: "Strategic Factors Influencing Target Prioritization in WWII Aerial Bombing"
+subtitle: "An Analysis of 1939-1945 Allied Targeting Against German Industrial Assets"
 author: 
